---
title: "Call Rate Analysis"
author: "Mike Wise"
date: "15 Mar 2017"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Data pre-processed and analyzied from call volume logs and web logs by Marcus Collins. 

Analysis based on R-Scripts from Jacob LaRiviere.

R-Markdown and plots from Mike Wise.

## Library Initialization
```{r, message=F}
library(tidyverse,quietly=T,warn.conflicts=F)
library(lubridate,quietly=T,warn.conflicts=F)
library(scales,quietly=T,warn.conflicts=F)
```

#### Set random seeds, record start time and version.

```{r}
set.seed(1234)
version <-0.2
versionstring <- sprintf("Version %.1f",version)

starttime <- Sys.time()
startfmttime <- sprintf(format(starttime, "%d %b %Y - %H:%M:%S"))

print(sprintf("%s created on %s",versionstring,startfmttime))
```

#### Various constants

```{r}
tztz <- "UTC"  # Apparently all of our time zones are UTC...
firstday <- as.POSIXct("2015-01-01",tz=tztz)  # we will count days from the first day in 2015

smcdates <- c("2016-08-17/red/0-30%","2016-09-1/red/30-50%","2016-09-07/red/50-100%")
xtotdates <- c("2016-10-11/purple/0-10%","2016-10-18/purple/10-30%","2016-11-01/purple/30-50%","2016-12-15/purple/50-90%",
              "2016-11-17/blue/content change")
totdates <- c(smcdates,xtotdates)
smcback <- "lightsteelblue1"
xbxback <- "darkseagreen2"
xabback <- "darkseagreen3"
totback <- "wheat"

fpath <- "../TorontoData"
sdate <- as.POSIXct("2016-06-01",tz=tztz)
mdate <- as.POSIXct("2017-01-01",tz=tztz)
edate <- as.POSIXct("2017-03-12",tz=tztz)
```

#### Misc utility functions

```{r}
addStepDateToVek <- function(dates,idx,dtvek,vvek){
  sar1 <- unlist(strsplit(dates[[idx]],"/"))
  datepart1 <- sar1[[1]]
  levpart1 <- sar1[[3]]
  if (!grepl("%",levpart1)){
    # if there is no % don't do anything
    return(vvek)
  }
  dt1 <- as.POSIXct(datepart1,tz=tztz)
  if (idx<length(dates)){
    sar2 <- unlist(strsplit(dates[[idx+1]],"/"))
    datepart2 <- sar2[[1]]
    dt2 <- as.POSIXct(datepart2,tz=tztz)
  } else {
    dt2 <- max(dtvek)
  }
  #print(dt1)
  #print(dt2)
  val <- as.numeric(gsub("%","",unlist(strsplit(levpart1,"-"))[[2]]))
  tochg <-  dt1<=dtvek & dtvek<= dt2
  vvek[ tochg ] <- val
  #print(sprintf("changed %d values to %d",sum(tochg),val))
  return(vvek)
}
getStepDates <- function(dates,dtvek){
 vvek <- rep(0,length(dtvek))
 for (i in 1:length(smcdates)){
   vvek <- addStepDateToVek(dates,i,dtvek,vvek)
 }
 return(vvek)
}
getSmcStepDates <- function(dtvek){
 return(getStepDates(smcdates,dtvek))
}
getXabStepDates <- function(dtvek){
 return(getStepDates(xtotdates,dtvek))
}


```


#### Plot Functions

Plots created using ggplot2


```{r}
addVlinesAndText <- function(vlines,gp){
  if (is.null(vlines)) return(gp) # do nothing in this case
  
  # split the lines and convert to data.frame
  sar <- strsplit(vlines,"/")
  # the following reforms the date strings into a data.frame for geom_vline
  ldf <- data.frame(t(matrix(unlist(sar),length(sar[[1]]),length(sar)))) #tricky
  names(ldf) <- c("dt","clr","lab")
  ldf$dt <- as.POSIXct(ldf$dt,tz=tztz)
  ldf$ndt <- as.numeric(ldf$dt)
  # add a newline to the front so as to display the text 
  # this keeps the text from writing on top of the vline
  
  ldf$lab <- paste0("\n",ldf$lab) 
  # now actually add the verticle lines and the text 
  gp <- gp + geom_vline(xintercept=ldf$ndt,color=ldf$clr) +
             annotate(geom="text",x=ldf$dt,y=0,label=ldf$lab,color=ldf$clr,hjust=0,angle=90)
  return(gp)
}
addBackground <- function(backg,gp){
  if (is.null(backg)) return(gp) # do nothing in this case
  gp <- gp + theme(panel.background = element_rect(fill = backg))
  return(gp)
}
dailyplot <- function(ddf,x,y,mtit="",xlab="date",ylab=NULL,vlines=NULL,backg=NULL,series=NULL){
  # Single series plot  with monthly breaks on the x-axis
  
  gp <- ggplot(ddf,aes_string(x=x,y=y)) + 
             geom_line(aes_string(color=series),na.rm=T)  +
             xlab(xlab) + ylab(ylab) + ggtitle(mtit) +
             scale_x_datetime("Date",breaks = date_breaks("1 months"),limits=c(sdate,edate))

  gp <- addVlinesAndText(vlines,gp)

  gp <- addBackground(backg,gp)

  return(gp)
}
```


## Read in call volume data

```{r}

readCallVolume <- function(frdate,todate,fname){
  cfname <- sprintf("%s/%s",fpath,fname)
  cvdf <- read.csv(cfname)  
  temp_date<- as.POSIXct(cvdf$Date,format="%m/%d/%Y %I:%M:%S %p",tz=tztz)
  temp_datehour<- as.POSIXct(cvdf$DateHour,format="%m/%d/%Y %I:%M:%S %p",tz=tztz)

  cvdf  <- cvdf %>% mutate( dt = temp_datehour) %>%
                    mutate( dnum = round(as.numeric(difftime(temp_date,firstday,"days")))) %>%
                    mutate( hnum = dnum*24 + hour(dt)) %>%
                    arrange( dt ) # sort

  n1 <- nrow(cvdf)
  cvdf <- cvdf %>% filter( frdate<=dt & dt<todate)
  n2 <- nrow(cvdf)
  print(sprintf("Read %d of %d lines from %s",n2,n1,cfname))
  
  return(cvdf)
}

cvdf1 <- readCallVolume(sdate,mdate,"genesys_ivr_call_data.csv")
cvdf2 <- readCallVolume(mdate,edate,"genesys_ivr_call_data-12.3.2017.csv")
cvdf <- rbind(cvdf1,cvdf2)

cvdf <- cvdf %>% filter( COUNTRY_NAME=="United States" ) %>% arrange( dt )

print(sprintf("Rows after filtering to United States only: %d",nrow(cvdf)))
```


## Total call volume plots

```{r fig.width=14, fig.height=6, echo=T}

ecdf <- cvdf %>% group_by(dnum) %>% 
                 summarise(dt=min(dt),Windows=sum(WindowsCalls),Xbox=sum(XboxTotalCalls),Xab=sum(XboxABCalls)) %>%
                 mutate( dnum=NULL ) %>% # delete dnum col
                 gather(series,count,-dt)

dailyplot(ecdf,"dt","count",series="series",mtit="Total Call Volumne - Windows vs. XBOX vs. XBOX AB",ylab="Count",vlines=totdates,backg=totback)
```
```{r fig.width=14, fig.height=6, echo=T}
ecdf <- cvdf %>% group_by(dnum) %>% 
                 summarise(dt=min(dt),Windows=sum(WindowsToAgentCalls),Xbox=sum(XboxTotalToAgentCalls),Xab=sum(XboxABToAgentCalls)) %>%
                 mutate( dnum=NULL ) %>% # delete dnum col
                 gather(series,count,-dt)

dailyplot(ecdf,"dt","count",series="series",mtit="To Agent Volume - Windows vs. XBOX vs. XBOX AB",ylab="Count",vlines=totdates,backg=totback)
```


## Read in SMC Active User/Session data

```{r}
readSessionVolume <- function(frdate,todate,fname){
  sfname <- sprintf("%s/%s",fpath,fname)
  svdf <- read.csv(sfname)  

  temp_dstr   <- sprintf("%d-%2.2d-%2.2d %2.2d",svdf$EventUtcYear,svdf$EventUtcMonth,svdf$EventUtcDay,svdf$EventUtcHour)
  temp_dtd   <- as.POSIXct(temp_dstr,format="%Y-%m-%d",tz=tztz)


  svdf <- svdf %>% mutate( dt=as.POSIXct(temp_dstr,format="%Y-%m-%d %H",tz="UTC") ) %>%
                   mutate( dnum=round(as.numeric(difftime(temp_dtd,firstday,"days"))) ) %>%
                   mutate( hnum  = dnum*24 + hour(dt) )

  n1 <- nrow(svdf)
  cvdf <- svdf %>% filter( frdate<=dt & dt<todate)
  n2 <- nrow(svdf)
  print(sprintf("Read %d of %d lines from %s",n2,n1,sfname))
  return(svdf)
}
svdf1 <- readSessionVolume(sdate,mdate,"hourly-smc-traffic.csv")
svdf2 <- readSessionVolume(sdate,mdate,"hourly-smc-traffic-2017.csv")

svdf <- rbind(svdf1,svdf2)

svdf <- svdf %>% arrange(dt) %>%                          # sort
                 filter( HourlyActiveSessions>1000 ) %>%  # plausiblity check mitigates range overflow in following plots
                 filter(sdate<=dt) %>%                    # get rid of everything before start date
                 mutate(spuration = HourlyActiveSessions / HourlyActiveUsers)
print(sprintf("Total SessionVolume rows:%d",nrow(svdf)))
```

## Total Hourly Active Sessions

```{r fig.width=14, fig.height=6, echo=F}
#sdate <- as.POSIXct("2016-10-07",tz=tztz) - dirty hack for debugging, allows a zoom 
#edate <- as.POSIXct("2016-10-10",tz=tztz)
dailyplot(svdf,"dt","HourlyActiveSessions",mtit="SMC - Hourly Active Sessions",ylab="Count",vlines=totdates,backg=totback)
```


## Total Active User/Session data
```{r fig.width=14, fig.height=6, echo=T}
mergeCallAndSessions <- function(cdf,sdf){
  
  cdf1 <- cdf %>% group_by(hnum) %>% summarize(WindowsCalls           = sum(WindowsCalls),
                                                XboxTotalCalls        = sum(XboxTotalCalls),
                                                XboxABCalls           = sum(XboxABCalls),
                                                WindowsToAgentCalls   = sum(WindowsToAgentCalls),
                                                XboxTotalToAgentCalls = sum(XboxTotalToAgentCalls),
                                                XboxABToAgentCalls    = sum(XboxABToAgentCalls)
                                                )
  
  # merge and order
  hdf <- inner_join(sdf,cdf1,by="hnum") %>% arrange(dt)

  hdf <- hdf %>% mutate( WindowsCallsPerSession           = WindowsCalls   / HourlyActiveSessions ) %>%
                 mutate( XboxTotalCallsPerSession         = XboxTotalCalls / HourlyActiveSessions ) %>%
                 mutate( XboxABCallsPerSession            = XboxABCalls    / HourlyActiveSessions ) %>%
                 mutate( WindowsToAgentCallsPerSession    = WindowsToAgentCalls   / HourlyActiveSessions ) %>%
                 mutate( XboxTotalToAgentCallsPerSession  = XboxTotalToAgentCalls / HourlyActiveSessions ) %>%
                 mutate( XboxABToAgentCallsPerSession     = XboxABToAgentCalls    / HourlyActiveSessions ) 

  # now do the daily set
  ddf <-hdf %>% group_by(dnum)  %>% summarise(dt=min(dt),
                                              ActiveSessions        = sum(HourlyActiveSessions),
                                              WindowsCalls          = sum(WindowsCalls),
                                              XboxTotalCalls        = sum(XboxTotalCalls),
                                              XboxABCalls           = sum(XboxABCalls),
                                              WindowsToAgentCalls   = sum(WindowsToAgentCalls),
                                              XboxTotalToAgentCalls = sum(XboxTotalToAgentCalls),
                                              XboxABToAgentCalls    = sum(XboxABToAgentCalls)
                                              )
  
  ddf <- ddf %>% mutate( WindowsCallsPerSession   = WindowsCalls   / ActiveSessions ) %>%
                 mutate( XboxTotalCallsPerSession = XboxTotalCalls / ActiveSessions ) %>%
                 mutate( XboxABCallsPerSession    = XboxABCalls    / ActiveSessions ) %>%
                 mutate( WindowsToAgentCallsPerSession   = WindowsToAgentCalls   / ActiveSessions ) %>%
                 mutate( XboxTotalToAgentCallsPerSession = XboxTotalToAgentCalls / ActiveSessions ) %>%
                 mutate( XboxABToAgentCallsPerSession    = XboxABToAgentCalls    / ActiveSessions ) 

  rv <- list(hdf=hdf,ddf=ddf)
  return(rv)
}

rv <- mergeCallAndSessions(cvdf,svdf)
htdf <- rv$hdf
dtdf <- rv$ddf
```

## Total call rate per session plots

```{r fig.width=14, fig.height=6, echo=T}
df1 <- dtdf %>% filter( WindowsCallsPerSession<1 )
mtit <- "Total - Call Rates - WindowsCalls Per Session - Daily Aggregated"
dailyplot(df1,"dt","WindowsCallsPerSession",mtit=mtit,ylab="Calls/Session",vlines=smcdates,backg=smcback)
```
```{r fig.width=14, fig.height=6, echo=T}
df1 <- dtdf %>% filter( WindowsCallsPerSession<1 )
mtit <- "Total - Call Rates - XBox Calls Per Session - Daily Aggregated"
dailyplot(df1,"dt","XboxTotalCallsPerSession",mtit=mtit,ylab="Calls/Session",vlines=xtotdates,backg=xbxback)
```
```{r fig.width=14, fig.height=6, echo=T}
df1 <- dtdf %>% filter( WindowsCallsPerSession<1 )
mtit <- "Total - Call Rates - XBox AB Calls Per Session - Daily Aggregated"
dailyplot(df1,"dt","XboxABCallsPerSession",mtit=mtit,ylab="Calls/Session",vlines=xtotdates,backg=xabback)
```

## To agent call rate per session plots


```{r fig.width=14, fig.height=6, echo=T}
df1 <- dtdf %>% filter( WindowsToAgentCallsPerSession<1 )
mtit <- "Total - Call Rates - To Agent WindowsCalls Per Session - Daily Aggregated"
dailyplot(df1,"dt","WindowsToAgentCallsPerSession",mtit=mtit,ylab="Calls/Session",vlines=smcdates,backg=smcback)
```
```{r fig.width=14, fig.height=6, echo=T}
df1 <- dtdf %>% filter( WindowsCallsPerSession<1 )
mtit <- "Total - Call Rates - To Agent XBox Calls Per Session - Daily Aggregated"
dailyplot(df1,"dt","XboxTotalToAgentCallsPerSession",mtit=mtit,ylab="Calls/Session",vlines=xtotdates,backg=xbxback)
```
```{r fig.width=14, fig.height=6, echo=T}
df1 <- dtdf %>% filter( WindowsCallsPerSession<1 )
mtit <- "Total - Call Rates - To Agent XBox AB Calls Per Session - Daily Aggregated"
dailyplot(df1,"dt","XboxABToAgentCallsPerSession",mtit=mtit,ylab="Calls/Session",vlines=xtotdates,backg=xabback)
```


## Done

```{r echo=F}
elap <- as.numeric((Sys.time()-starttime)[1],units="secs")
print(sprintf("%s created on %s took %.1f secs",versionstring,startfmttime,elap))
```