---
title: "Chat Log Data Analysis"
author: "Mike Wise"
date: "2 Mar 2017"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Data pre-processed and analyzied from chat logs and web logs by Marcus Collins. 

Analysis based on R-Scripts from Jacob LaRiviere.

R-Markdown and plots from Mike Wise.

## Initialization of libraries
```{r, message=F}
library(tidyverse,quietly=T,warn.conflicts=F)
library(lubridate,quietly=T,warn.conflicts=F)
library(scales,quietly=T,warn.conflicts=F)
```

Set random seeds, record start time and version.

```{r}
set.seed(1234)
version <-0.5
versionstring <- sprintf("Version %.1f",version)

starttime <- Sys.time()
startfmttime <- sprintf(format(starttime, "%d %b %Y - %H:%M:%S"))

print(sprintf("%s created on %s",versionstring,startfmttime))
```

```{r}
tztz <- "UTC"  # Apparently all of our time zones are UTC...
firstday <- as.POSIXct("2015-01-01",tz=tztz)  # we will count days from the first day in 2015

smcdates <- c("2016-08-17/red/0-30%","2016-09-1/red/30-50%","2016-09-07/red/50-100%")
xabdates <- c("2016-10-11/purple/0-10%","2016-10-18/purple/10-30%","2016-11-01/purple/30-50%","2016-12-15/purple/50-90%",
              "2016-11-17/blue/content change")
totdates <- c(smcdates,xabdates)
smcback <- "lightsteelblue1"
xabback <- "darkseagreen2"
totback <- "wheat"

addStepDate <- function(dates,idx,dtvek,vvek){
  sar1 <- unlist(strsplit(dates[[idx]],"/"))
  dt1 <- as.POSIXct(sar1[[1]],tz=tztz)
  if (idx<length(dates)){
    sar2 <- unlist(strsplit(dates[[idx+1]],"/"))
    dt2 <- as.POSIXct(sar2[[1]],tz=tztz)
  } else {
    dt2 <- max(dtvek)
  }
  #print(dt1)
  #print(dt2)
  val <- as.numeric(gsub("%","",unlist(strsplit(sar1[[3]],"-"))[[2]]))
  tochg <-  dt1<=dtvek & dtvek<= dt2
  vvek[ tochg ] <- val
  #print(sprintf("changed %d values to %d",sum(tochg),val))
  return(vvek)
}
addSmcStepDates <- function(dtvek,vvek=NULL){
  if (is.null(vvek)){
    vvek <- rep(0,length(dtvek))
  }
  for (i in 1:length(smcdates)){
    vvek <- addStepDate(smcdates,i,dtvek,vvek)
  }
  return(vvek)
}
addXabStepDates <- function(dtvek,vvek=NULL){
  xabdates1 <- xabdates[1:(length(xabdates)-1)]
  if (is.null(vvek)){
    vvek <- rep(0,length(dtvek))
  }
  for (i in 1:length(xabdates1)){
    vvek <- addStepDate(xabdates1,i,dtvek,vvek)
  }
  return(vvek)
}
```

## Read in chat volume data

```{r}
fname <- "../data/chat_volume_duration_features-Aug2016-current.csv"
sdate <- as.POSIXct("2016-06-01",tz=tztz)
edate <- as.POSIXct("2017-01-15",tz=tztz)


cvdf <- read.csv(fname)
cvdf$BlockBeginTime1 <- gsub("3/13/2016 2:","3/13/2016 3:",cvdf$BlockBeginTime)
cvdf$DateHour1 <- gsub("3/13/2016 2:","3/13/2016 3:",cvdf$DateHour)
cvdf$bbt <- as.POSIXct(cvdf$BlockBeginTime1,format="%m/%d/%Y %I:%M:%S %p",tz=tztz)
cvdf$dtd <- as.POSIXct(cvdf$Date,format="%m/%d/%Y %I:%M:%S %p",tz=tztz)
cvdf$dt <- as.POSIXct(cvdf$DateHour1,format="%m/%d/%Y %I:%M:%S %p",tz=tztz)
cvdf$dnum <- round(as.numeric(difftime(cvdf$dtd,firstday,"days")),0)
cvdf$hnum <- cvdf$dnum*24 + hour(cvdf$dt)

# Just USA
cvdf <- cvdf[cvdf$CountryCode=="USA",]

# get rid of everything before the stard date
print(sprintf("Rows before filtering from %s were %d",sdate,nrow(cvdf)))
cvdf <- cvdf[cvdf$dt>=sdate,]
print(sprintf("Rows after  filtering from %s were %d",sdate,nrow(cvdf)))
```


Functions.


```{r}
dailyplot <- function(x,y,mtit="",xlab="date",ylab=NULL,vlines=NULL,backg=NULL){
  # Single series plot  with monthly breaks on the x-axis
  ymax <- max(y)*1.05
  ddf <- data.frame(x=x,y=y)
  gp <- ggplot(ddf) + geom_line(aes(x,y),na.rm=T)  +
            xlab(xlab) + ylab(ylab) + ggtitle(mtit) +
            scale_y_continuous(limits=c(0,ymax)) +
            scale_x_datetime("Date",breaks = date_breaks("1 months"),limits=c(sdate,edate))
  if (!is.null(vlines)){
    # split the lines and convert to data.frame
    sar <- strsplit(vlines,"/")
    # the following reforms the date strings into a data.frame for geom_vline
    ldf <- data.frame(t(matrix(unlist(sar),length(sar[[1]]),length(sar))))
    names(ldf) <- c("dt","clr","lab")
    ldf$dt <- as.POSIXct(ldf$dt,tz=tztz)
    ldf$ndt <- as.numeric(ldf$dt)
    ldf$lab <- paste0("\n",ldf$lab)
    gp <- gp + geom_vline(xintercept=ldf$ndt,color=ldf$clr) +
               annotate(geom="text",x=ldf$dt,y=0,label=ldf$lab,color=ldf$clr,hjust=0,angle=90)
  }
  if (!is.null(backg)){
     gp <- gp + theme(panel.background = element_rect(fill = backg))
  }
  return(gp)
}
dailyplot2 <- function(x,y,z,mtit="",xlab="date",ylab=NULL,vlines=NULL,backg=NULL){
  # Multiple  plot over a day with monthly breaks on the x-axis
  zlab <- substitute(z)
  ymax <- max(y)*1.05
  ddf <- data.frame(x=x,y=y,z=z)
  names(ddf)[3] <- as.character(zlab)
  print(head(ddf))
  gp <- ggplot(ddf,aes(x,y)) + geom_line(aes_string(color=zlab),na.rm=T) +
            xlab(xlab) + ylab(ylab) + ggtitle(mtit) +
            scale_y_continuous(limits=c(0,ymax)) +
            scale_x_datetime("Date",breaks = date_breaks("1 months"),limits=c(sdate,edate))
  if (!is.null(vlines)){
    # split the lines and convert to data.frame
    sar <- strsplit(vlines,"/")
    # the following reforms the date strings into a data.frame for geom_vline
    ldf <- data.frame(t(matrix(unlist(sar),length(sar[[1]]),length(sar))))
    names(ldf) <- c("dt","clr","lab")
    ldf$dt <- as.POSIXct(ldf$dt,tz=tztz)
    ldf$ndt <- as.numeric(ldf$dt)
    ldf$lab <- paste0("\n",ldf$lab)
    gp <- gp + geom_vline(xintercept=ldf$ndt,color=ldf$clr) +
               annotate(geom="text",x=ldf$dt,y=0,label=ldf$lab,color=ldf$clr,hjust=0,angle=90)
  }
  if (!is.null(backg)){
     gp <- gp + theme(panel.background = element_rect(fill = backg))
  }
  return(gp)
}
```


## Xbox vs. SMC Entry count

Note that IsSMX and IsSMC are almost mutually exclusive, so we split them

```{r fig.width=14, fig.height=6, echo=T}
xtabs(~ IsSMC + IsSXC,cvdf)
smcdf <- cvdf[cvdf$IsSMC=="True",]
smcdf <- cvdf
sxcdf <- cvdf[cvdf$IsSXC=="True",]
#smcdf <- smcdf[smcdf$Subject=="TS - Windows",]
print(sprintf("smcdf rows:%d",nrow(smcdf)))
print(sprintf("sxcdf rows:%d",nrow(sxcdf)))
xvsdf <- cvdf %>% group_by(dnum,IsSMC) %>% summarise(dt=min(dt),count=n())
series <- xvsdf$IsSMC
series <- gsub("False","XBOX",series)
series <- gsub("True","SMC",series)
dailyplot2(xvsdf$dt,xvsdf$count,series,"Total - SMC vs. XBOX",ylab="Count",vlines=totdates,backg=totback)
```


## SMC daily plots
```{r fig.width=14, fig.height=6, echo=T}
df <- smcdf %>% group_by(dnum) %>% summarize(dt=min(dt),cib = sum(ChatsInBlock))
dailyplot(df$dt,df$cib,"SMC - Chats In Block",ylab="Sum",vlines=smcdates,backg=smcback)
```


```{r fig.width=14, fig.height=6, echo=T}
df <- smcdf %>% group_by(dnum) %>% summarize(dt=min(dt),cmins = sum(ChatsInBlock*MeanChatDuration) )
dailyplot(df$dt,df$cmins,"SMC - Chat Minutes",ylab="Sum",vlines=smcdates,backg=smcback)
```


```{r fig.width=14, fig.height=6, echo=T}
df <- smcdf %>% group_by(dnum) %>% summarize(dt=min(dt),entrycount = n())
dailyplot(df$dt,df$entrycount,"SMC - Entry Count",ylab="Count",vlines=smcdates,backg=smcback)
```

## SXC daily plot

```{r fig.width=14, fig.height=6, echo=T}
df <- sxcdf %>% group_by(dnum) %>% summarize(dt=min(dt),cib = sum(ChatsInBlock) )
dailyplot(df$dt,df$cib,"SXC - Chats In Block",ylab="Sum",vlines=xabdates,backg=xabback)
```
```{r fig.width=14, fig.height=6, echo=T}
df <- sxcdf %>% group_by(dnum) %>% summarize(dt=min(dt),cmins = sum(ChatsInBlock*MeanChatDuration) )
dailyplot(df$dt,df$cmins,"SXC - Chat Minutes",ylab="Sum",vlines=xabdates,backg=xabback)
```
```{r fig.width=14, fig.height=6, echo=T}
df <- sxcdf %>% group_by(dnum) %>% summarize(dt=min(dt),entrycount=n() )
dailyplot(df$dt,df$entrycount,"SXC - Entry Count",ylab="Count",vlines=xabdates,backg=xabback)
```





```{r fig.width=14, fig.height=6, echo=T}
df <- smcdf %>% group_by(dnum,virtualAgent) %>% summarize(dt=min(dt),count = n() )
df$dt <- as.POSIXct(as.Date(df$dt,tz=tztz),tz=tztz) # trunc to 0:00
virtualAgent <- df$virtualAgent
dailyplot2(df$dt,df$count,virtualAgent,"SMC - virtualAgent",ylab="Count",vlines=smcdates,backg=smcback)
```
```{r fig.width=14, fig.height=6, echo=T}
df1 <- df %>% group_by(dnum) %>% summarize(dt=min(dt),count=sum(count)) 
df1$falseCount <- df[df$virtualAgent=="False",]$count
df1$fracVirtual <- 100*(1-df1$falseCount/df1$count)
df1$fracVirtualSoll <- addSmcStepDates(df1$dt)
df2 <- df1 %>% gather(series,pct,fracVirtual:fracVirtualSoll,-dt)
series <- df2$series
dailyplot2(df2$dt,df2$pct,series,"SMC - virtualAgent Percentage",ylab="Percent",vlines=smcdates,backg=smcback)
```

```{r fig.width=14, fig.height=6, echo=T}
df1 <- df %>% group_by(dnum) %>% summarize(dt=min(dt),count=sum(count)) 
df1$dt <- as.POSIXct(as.Date(df1$dt,tz=tztz),tz=tztz) # trunc to 0:00
df1$falseCount <- df[df$virtualAgent=="False",]$count
df1$fracVirtual <- 100*(1-df1$falseCount/df1$count)
df1$fracVirtualSoll <- addXabStepDates(df1$dt)
df2 <- df1 %>% gather(series,pct,fracVirtual:fracVirtualSoll,-dt)
series <- df2$series
df2 <- df2[ order(df2$series,df2$dt),]
dailyplot2(df2$dt,df2$pct,series,"SXC - virtualAgent Percentage",ylab="Percent",vlines=xabdates,backg=xabback)
```
## Read inSMC Active User/Session data
```{r}
svfname <- "../data/hourly-smc-traffic.csv"
svdf <- read.csv(svfname)
svdf$sdt <- sprintf("%d-%2.2d-%2.2d %2.2d",svdf$EventUtcYear,svdf$EventUtcMonth,svdf$EventUtcDay,svdf$EventUtcHour)
svdf$dtutc <- as.POSIXct(svdf$sdt,format="%Y-%m-%d %H",tz="UTC")
svdf$dt <- as.POSIXct(svdf$dtutc,tz=tztz)
svdf$dtd <- as.POSIXct(svdf$sdt,format="%Y-%m-%d",tz=tztz)
svdf$dnum <- round(as.numeric(difftime(svdf$dtd,as.POSIXct("2015-01-01",tz=tztz),"days")),0)
svdf$hnum <- svdf$dnum*24 + hour(svdf$dt)
svdf <- svdf[ order(svdf$dt),]
svdf <- svdf[ svdf$HourlyActiveSessions>1000,]  # fail plausiblity
  
# get rid of everything before July 2016
print(sprintf("Rows before filtering from %s were %d",sdate,nrow(svdf)))
svdf <- svdf[svdf$dt>=sdate,]
print(sprintf("Rows after  filtering from %s were %d",sdate,nrow(svdf)))
svdf$spuratio <- svdf$HourlyActiveSessions / svdf$HourlyActiveUsers


```

## Total Hourly Active Sessions
```{r fig.width=14, fig.height=6, echo=F}
#sdate <- as.POSIXct("2016-10-07",tz=tztz)
#edate <- as.POSIXct("2016-10-10",tz=tztz)
dailyplot(svdf$dt,svdf$HourlyActiveSessions,"SMC - Hourly Active Sessions",ylab="Count",vlines=totdates,backg=totback)
```


## Total Active User/Session data
```{r fig.width=14, fig.height=6, echo=T}
mergeChatAndSessions <- function(cdf,sdf,filtSMC=NULL){
  
  if (!is.null(filtSMC)){
    cdf <- cdf[ cdf$IsSMC==filtSMC,]
  }
  
  # cut down on colums and group by hour
  cdf1 <- cdf[,c("hnum","CumulativeChatDuration","ChatsInBlock","MeanChatDuration")]
  cdf1 <- cdf1 %>% group_by(hnum) %>% summarize(CumulativeChatDuration=sum(CumulativeChatDuration),ChatsInBlock=sum(ChatsInBlock))
  
  # merge and order
  hdf <- merge(sdf,cdf1, by="hnum")
  hdf <- hdf[order(hdf$dt), ]

  # calc a few extras
  hdf$chatMinPerSession <- hdf$CumulativeChatDuration / hdf$HourlyActiveSessions
  hdf$chatsPerSession   <- hdf$ChatsInBlock           / hdf$HourlyActiveSessions
  
  # now do the daily set
  ddf <-hdf %>% group_by(dnum)  %>% summarise(dt=min(dt),ChatsInBlock=sum(ChatsInBlock),chatMinPerSession=mean(chatMinPerSession),
                                     CumulativeChatDuration=sum(CumulativeChatDuration),ActiveSessions=sum(HourlyActiveSessions))
  
  ddf$chatMinPerSession <- ddf$CumulativeChatDuration / ddf$ActiveSessions
  ddf$chatsPerSession   <- ddf$ChatsInBlock           / ddf$ActiveSessions
  
  rv <- list()
  rv$hdf <- hdf
  rv$ddf <- ddf
  return(rv)
}

rv <- mergeChatAndSessions(cvdf,svdf)
htdf <- rv$hdf
dtdf <- rv$ddf

srv <- mergeChatAndSessions(cvdf,svdf,"True")
hsdf <- srv$hdf
dsdf <- srv$ddf

xrv <- mergeChatAndSessions(cvdf,svdf,"False")
hxdf <- xrv$hdf
dxdf <- xrv$ddf
```

## Total - Rate per Session Plots
```{r fig.width=14, fig.height=6, echo=T}
temp <- dtdf[ dtdf$chatsPerSession<0.015,]
dailyplot(temp$dt,temp$chatsPerSession,"Total - Rates - Chats Per Session - Daily Aggregated",ylab="Chats/Session",vlines=totdates,backg=totback)
```
```{r fig.width=14, fig.height=6, echo=T}
dsdf$series <- "SMC"
dxdf$series <- "XBOX"
ddf <- rbind(dsdf,dxdf)
temp <- ddf[ ddf$chatsPerSession<0.015,]
series <- temp$series
dailyplot2(temp$dt,temp$chatsPerSession,series,"Total - Rates - Chats Per Session - Daily Aggregated",ylab="Chats/Session",vlines=totdates,backg=totback)
```


```{r fig.width=14, fig.height=6, echo=T}
temp <- htdf[ htdf$chatsPerSession<0.015,]
#scut <- as.POSIXct("2016-08-15",tz=tztz)
#ecut <- as.POSIXct("2016-09-15",tz=tztz)
#temp <- temp[scut <= temp$dt & temp$dt <= ecut,] 
dailyplot(temp$dt,temp$chatsPerSession,"Total - Rates - Chats Per Session - Hourly Aggregated",ylab="Chats/Session",vlines=totdates,backg=totback)
```
```{r fig.width=14, fig.height=6, echo=T}
temp <- dtdf[ dtdf$chatMinPerSession<1.0,]
dailyplot(temp$dt,temp$chatMinPerSession,"Total - Rates - Chat Minutes Per Session - Daily Aggregation",ylab="Minutes/Session",vlines=totdates,backg=totback)
```
```{r fig.width=14, fig.height=6, echo=T}
dsdf$series <- "SMC"
dxdf$series <- "XBOX"
ddf <- rbind(dsdf,dxdf)
temp <- ddf[ ddf$chatsPerSession<0.015,]
series <- temp$series
dailyplot2(temp$dt,temp$chatMinPerSession,series,"Total - Rates - Chats Minutes Per Session - Daily Aggregated",ylab="Chats/Session",vlines=totdates,backg=totback)
```
```{r fig.width=14, fig.height=6, echo=T}
temp <- htdf[ htdf$chatMinPerSession<1.0,]
dailyplot(temp$dt,temp$chatMinPerSession,"Total - Rates - Chat Minutes Per Session - Hourly Aggregation",ylab="Minutes/Session",vlines=totdates,backg=totback)
```

## Done
```{r echo=F}
elap <- as.numeric((Sys.time()-starttime)[1],units="secs")
print(sprintf("%s created on %s took %.1f secs",versionstring,startfmttime,elap))
```