---
title: "Experiments Early 2017 - Plot Visualzations"
author: "Mike Wise"
date: "27 April 2017"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

hook_output <- knitr::knit_hooks$get("output")
knitr::knit_hooks$set(output=function(x,options){
  xn <- hook_output(x,options)
  # interestingly xn is a big character string. 
  # I had expected a list or vector, but the length of x is 1 and the class is character.

  # The following regexp extracts the parameters from a statement of the form
  # htmlesc<<(pat1,pat2)>> and converts it to <pat1>pat2</pat1>
  xn <- gsub("## htmlesc<<([^,]*),{1}([^>>]*)>>","\n```\n<\\1>\\2</\\1>\n```\n",xn)
  # now remove double escaped lines that occur when we do these right after each other
  gsub(">\n```\n\n\n```\n<",">\n<",xn)
}
)

hook_warn <- knitr::knit_hooks$get("warning")
knitr::knit_hooks$set(warning = function(x,options){
  xn <- hook_warn(x,options)
  xn <- NULL
  xn
}
)
```

Data pre-processed and analyzied from call volume logs and web logs by Marcus Collins. 

Analysis based on R-Scripts from Jacob LaRiviere.

R-Markdown, regression code, and plots from Mike Wise.

## Library Initialization
```{r, message=F}
library(tidyverse,quietly=T,warn.conflicts=F)
library(lubridate,quietly=T,warn.conflicts=F)
library(scales,quietly=T,warn.conflicts=F)
library(gridExtra,quietly=T,warn.conflicts = F)

options(warn=-1) # get rid of tiresome mismatched timezone warnings (I know already)
```

#### Set random seeds, record start time and version.

```{r}
set.seed(1234)
version <-0.2
versionstring <- sprintf("Version %.1f",version)

starttime <- Sys.time()
startfmttime <- sprintf(format(starttime, "%d %b %Y - %H:%M:%S"))

print(sprintf("%s created on %s",versionstring,startfmttime))
```

#### Various constants

```{r}
tztz <- "UTC"            # these are for server log datetimes
tzbk <- "US/Pacific"     # these are for mostly datetimes reported by people

firstday <- as.POSIXct("2015-01-01",tz=tztz)  # we will count days from the first day in 2015


smcb1dates <- c("2017-03-08 06:03/blue/-ok-/2017-03-08 07:57",
                "2017-03-11 08:01/blue/-ok-/2017-03-11 09:00",
                "2017-03-14 01:02/blue/-ok-/2017-03-14 03:10",
                "2017-03-15 06:11/blue/-ok-/2017-03-15 08:24",
                "2017-03-18 08:04/blue/-ok-/2017-03-18 09:08",
                "2017-03-20 06:04/blue/-ok-/2017-03-20 08:02")

smcb2dates <- c("2017-04-17 06:00/purple/-ok-/2017-04-17 08:00",
                "2017-04-17 19:00/purple/-ok-/2017-04-17 20:00",
                "2017-04-18 01:00/purple/-ok-/2017-04-18 03:00",
                "2017-04-18 17:00/purple/-ok-/2017-04-18 18:00",
                "2017-04-19 06:00/purple/- turned back on for 15 min -/2017-04-19 08:00",
                "2017-04-19 20:00/purple/-ok-/2017-04-19 21:00",
                "2017-04-20 13:25/purple/- not hourly aligned -/2017-04-20 14:30",
                "2017-04-22 08:00/purple/- missed? -/2017-04-22 09:00",
                "2017-04-22 20:30/purple/- not hourly aligned -/2017-04-22 21:30",
                "2017-04-23 06:00/purple/-ok-/2017-04-23 07:00",
                "2017-04-23 19:00/purple/-ok-/2017-04-23 20:00")

smcb1sdate <- as.POSIXct("2017-03-08",tz=tzbk)
smcb1edate <- smcb1sdate+14*24*3600

smcb2sdate <- as.POSIXct("2017-04-17",tz=tzbk)
smcb2edate <- smcb2sdate+8*24*3600

totdates <- c(smcb1dates,smcb2dates)

smcback <- "lightsteelblue1"
xbxback <- "darkseagreen2"
xabback <- "darkseagreen3"
totback <- "wheat"

fpath <- "TorontoData1"
sdate <- as.POSIXct("2017-03-08",tz=tztz)
edate <- as.POSIXct("2017-04-24",tz=tztz)
```

#### Misc utility functions

```{r}

s2date <- function(strdate){
  return(as.POSIXct(strdate,tz=tzbk))
}
crackdate <- function(datestr){
  sar <- unlist(strsplit(datestr,"/"))
  ssdate <- sar[[1]]
  sdate <- s2date(ssdate)
  if (length(sar)>=4){
    sedate <- sar[[4]]
    edate <- s2date(sedate)
  } else {
    sedate <- NULL
    edate <- NULL
  }
  val <- 0
  sval <- sar[[3]]
  levpart <- sar[[3]]
  pctpresent <- F
  if (grepl("%",levpart)){
    if (grepl("-",levpart)){
      levpart <- gsub("%","",levpart)
      val <- as.numeric(unlist(strsplit(levpart,"-"))[[2]])
      sval <- gsub("-","_",levpart)
      pctpresent <- T
    }
  }
  return(list(sdate=sdate,ssdate=ssdate,edate=edate,sedate=sedate,val=val,sval=sval,pctpresent=pctpresent))
}

addStepDateToVek <- function(dates,idx,dtvek,vvek){
  cd1 <- crackdate(dates[[idx]])
  if (!cd1$pctpresent){
    # if there is no % don't do anything
    return(vvek)
  }
  dt1 <- cd1$date
  if (idx<length(dates)){
    cd2 <- crackdate(dates[[idx+1]])
    dt2 <- cd2$sdate
  } else {
    dt2 <- max(dtvek)
  }
  #print("addstepdate")
  #print(dt1)
  #print(dt2)
  val <- cd1$val
  tochg <-  dt1<=dtvek & dtvek<= dt2
  vvek[ tochg ] <- val
  #print(sprintf("changed %d values to %d",sum(tochg),val))
  return(vvek)
}
getStepDates <- function(dates,dtvek){
 vvek <- rep(0,length(dtvek))
 for (i in 1:length(dates)){
   vvek <- addStepDateToVek(dates,i,dtvek,vvek)
 }
 return(vvek)
}
getSmcStepDates <- function(dtvek){
 return(getStepDates(smcdates,dtvek))
}
getXabStepDates <- function(dtvek){
 return(getStepDates(xbxdates,dtvek))
}
```


#### Plot Functions

Plots created using ggplot2


```{r}
addVlines2AndText <- function(vlines,gp,hjust=0){
  if (is.null(vlines)) return(gp) # do nothing in this case
  
  # split the lines and convert to data.frame
  sar <- strsplit(vlines,"/")
  # the following reforms the date strings into a data.frame for geom_vline
  ldf <- data.frame(t(matrix(unlist(sar),length(sar[[1]]),length(sar)))) #tricky
  names(ldf) <- c("dt","clr","lab","dt2")
  ldf$dt <- as.POSIXct(ldf$dt,tz=tzbk)
  ldf$fdt <- format(ldf$dt,format="%Y-%m-%d   %H%:%M %Z")
  ldf$ndt <- as.numeric(ldf$dt)
  ldf$dt2 <- as.POSIXct(ldf$dt2,tz=tzbk)
  ldf$fdt2 <- format(ldf$dt2,format="%Y-%m-%d   %H%:%M %Z")
  ldf$ndt2 <- as.numeric(ldf$dt2)
  # add a newline to the front so as to display the text 
  # this keeps the text from writing on top of the vline

  olab <- ldf$lab
  ldf$lab <- sprintf("\n%s  %s",ldf$fdt,olab)
  ldf$lab2 <- sprintf("\n%s  %s",ldf$fdt2,olab)
  # now actually add the verticle lines and the text 
  gp <- gp + geom_vline(xintercept=ldf$ndt,color=ldf$clr) + geom_vline(xintercept=ldf$ndt2,color=ldf$clr) +
             annotate(geom="text",x=ldf$dt,y=0,label=ldf$lab,color=ldf$clr,hjust=hjust,angle=90,na.rm=T) +
             annotate(geom="text",x=ldf$dt2,y=0,label=ldf$lab2,color=ldf$clr,hjust=hjust,angle=90,na.rm=T)
  return(gp)
}
addVlinesAndText <- function(vlines,gp,hjust=0){
  if (is.null(vlines)) return(gp) # do nothing in this case
  
  # split the lines and convert to data.frame
  sar <- strsplit(vlines,"/")
  # the following reforms the date strings into a data.frame for geom_vline
  ldf <- data.frame(t(matrix(unlist(sar),length(sar[[1]]),length(sar)))) #tricky
  names(ldf) <- c("dt","clr","lab")
  ldf$dt <- as.POSIXct(ldf$dt,tz=tztz)
  ldf$ndt <- as.numeric(ldf$dt)
  # add a newline to the front so as to display the text 
  # this keeps the text from writing on top of the vline
  
  ldf$lab <- paste0("\n",ldf$lab) 
  # now actually add the verticle lines and the text 
  gp <- gp + geom_vline(xintercept=ldf$ndt,color=ldf$clr) +
             annotate(geom="text",x=ldf$dt,y=0,label=ldf$lab,color=ldf$clr,hjust=hjust,angle=90,na.rm=T)
  return(gp)
}
addBackground <- function(backg,gp){
  if (is.null(backg)) return(gp) # do nothing in this case
  gp <- gp + theme(panel.background = element_rect(fill = backg))
  return(gp)
}
overdate <- function(ovdate,defdate){
  # date override
  rv <- defdate
  if (!is.null(ovdate)) { 
    rv <- ovdate
  }
  return(rv)
}
dailyplot <- function(ddf,x,y,mtit="",xlab="date",ylab=NULL,vlines=NULL,vlines2=NULL,backg=NULL,series=NULL,clrs=NULL,
                      hjust=0,rotxaxtxt=0,ovsdate=NULL,ovedate=NULL,dfmt="%Y-%m-%d",addpoints=F,customscale=T){
  # Single series plot  with monthly breaks on the x-axis
  
  # override dates if needed
  dpsdate <- overdate(ovsdate,sdate)
  dpedate <- overdate(ovedate,edate)
  
  if (customscale){
    ddf <- ddf %>% filter( dpsdate<=dt & dt<=dpedate )
  }
  
  
  
  gp <- ggplot(ddf,aes_string(x=x,y=y)) + 
             geom_line(aes_string(color=series),na.rm=T)  +
             xlab(xlab) + ylab(ylab) + ggtitle(mtit) +
             scale_x_datetime("Date",breaks = date_breaks("1 days"),
                              limits=c(dpsdate,dpedate),date_label=dfmt)

  if (addpoints){
    gp <- gp + geom_point(aes_string(color=series),na.rm=T)
  }
  if (!is.null(clrs)){
    gp <- gp + scale_color_manual(values=clrs)
  }
  gp <- addVlinesAndText(vlines,gp,hjust=hjust)
  gp <- addVlines2AndText(vlines2,gp,hjust=hjust)

  gp <- addBackground(backg,gp)
  
  if (rotxaxtxt!=0){
    gp <- gp + theme(axis.text.x = element_text(angle = rotxaxtxt, hjust = 0))
  }

  return(gp)
}
```
## Read in consolidated chat, call, and session volume data

```{r}
stload <- Sys.time()
tfname <- sprintf("%s/%s",fpath,"consolidatedEarly2017TorontoData01.csv")
condf <- read.csv(tfname)

# minsessfilt <- 5000
# nbef <- nrow(condf)
# condf <- condf %>% filter(minsessfilt<actsess)
# naft <- nrow(condf)
# print(sprintf("Filtered %d of %d hours because sessions less than %d",(nbef-naft),naft,minsessfilt))
condf <- condf %>% mutate( dt = as.POSIXct(dt,tz=tztz) ) %>%
                   mutate( log_winchib = log(winchib) ) %>%
                   mutate( log_wincall = log(wincall) ) %>%
                   mutate( log_xbxchib = log(xbxchib) ) %>%
                   mutate( log_xbxcall = log(xbxcall) ) %>%
                   mutate( rate_winchib = winchib/actsess ) %>%
                   mutate( rate_wincall = wincall/actsess ) %>%
                   mutate( rate_xbxchib = xbxchib/actsess ) %>%
                   mutate( rate_xtkchib = xtkchib/actsess ) %>%
                   mutate( rate_xabchib = xabchib/actsess ) %>%
                   mutate( rate_xbxcall = xbxcall/actsess ) %>%
                   mutate( rate_xtkcall = xtkcall/actsess ) %>%
                   mutate( rate_xabcall = xabcall/actsess ) %>%
                   mutate( xbxchibdiff = xabchib-xtkchib ) %>%
                   mutate( xbxcalldiff = xabcall-xtkcall ) %>%
                   mutate( rate_xbxchibdiff = rate_xabchib-rate_xtkchib ) %>%
                   mutate( rate_xbxcalldiff = rate_xabcall-rate_xtkcall ) 

# dcondf <- condf %>% group_by(dnum) %>% summarise(dt=min(dt),
#                                                  totchib=sum(totchib),winchib=sum(winchib),xbxchib=sum(xbxchib),
#                                                  totcall=sum(totcall),wincall=sum(wincall),xbxcall=sum(xbxcall),
#                                                  actsess=sum(actsess),actuser=sum(actuser)
#                                                  )

elap <- as.numeric((Sys.time()-stload)[1],units="secs")
print(sprintf("Loading consolidated data took %.1f secs",elap))
```
```{r fig.width=14, fig.height=6, echo=T}
pltdf <- condf %>% gather(series,chib,-dt) %>% filter(series %in% c("totchib","winchib","xbxchib"))
dailyplot(pltdf,"dt","chib",series="series",mtit="Chats In Block",ylab="Sum",vlines=totdates,backg=totback,rotxaxtxt=-30)
```
```{r fig.width=14, fig.height=6, echo=T}
pltdf <- condf %>% gather(series,call,-dt) %>% filter(series %in% c("totcall","wincall","xbxcall"))
dailyplot(pltdf,"dt","call",series="series",mtit="Calls",ylab="Sum",vlines=totdates,backg=totback,rotxaxtxt=-30)
```
```{r fig.width=14, fig.height=6, echo=T}
pltdf <- condf %>% gather(series,active,-dt) %>% filter(series %in% c("actsess","actuser"))
dailyplot(pltdf,"dt","active",series="series",mtit="Sessions",ylab="Sum",vlines=totdates,backg=totback,rotxaxtxt=-30)
```

## SMC Chats and Calls

```{r fig.width=14, fig.height=6, echo=T}
iplt <- 1
getmtit <- function(mtit,chkdt){
  nmtit <- sprintf("%d - %s -  %s",iplt,mtit,chkdt$ssdate)
  iplt <<- iplt+1
  nmtit
}

justdoone <- F
getstodo <- function(){
  if (justdoone){
    return(smcb1dates[1])
  }
  return(c(smcb1dates,smcb2dates))
}

stodo <- getstodo()
for (sdt in stodo){
  ckdt <- crackdate(sdt)
  pltdf <- condf %>% gather(series,chib,-dt) %>% filter(series %in% c("winchib","wincall"))
  print(dailyplot(pltdf,"dt","chib",series="series",mtit=getmtit("SMB Chats and Calls",ckdt),ylab="Sum",
                  vlines2=sdt,backg=smcback,rotxaxtxt=-30,dfmt="%Y-%m-%d %H:%M %Z",addpoints=T,
                  ovsdate=(ckdt$sdate-14*3600),ovedate=(ckdt$edate+14*3600)))
}
```


## XBox Chats

```{r fig.width=14, fig.height=6, echo=T}
stodo <- getstodo()
for (sdt in stodo){
  ckdt <- crackdate(sdt)
  pltdf <- condf %>% gather(series,chib,-dt) %>% filter(series %in% c("xbxchib","xtkchib","xabchib","xbxchibdiff"))
  clrs <- c("xbxchib"="blue","xtkchib"="darkgreen","xabchib"="purple","xbxchibdiff"="red")
  print(dailyplot(pltdf,"dt","chib",series="series",mtit=getmtit("XBOX Chats In Block",ckdt),ylab="Sum",addpoints=T,clrs=clrs,
                  vlines2=sdt,backg=xbxback,rotxaxtxt=-30,dfmt="%Y-%m-%d %H:%M %Z",
                  ovsdate=(ckdt$sdate-14*3600),ovedate=(ckdt$edate+14*3600)))
}
```

## XBox Calls

```{r fig.width=14, fig.height=6, echo=T}
stodo <- getstodo()
for (sdt in stodo){
  ckdt <- crackdate(sdt)
  pltdf <- condf %>% gather(series,chib,-dt) %>% filter(series %in% c("xbxcall","xtkcall","xabcall","xbxcalldiff"))
  clrs <- c("xbxcall"="blue","xtkcall"="darkgreen","xabcall"="purple","xbxcalldiff"="red")
  
  print(dailyplot(pltdf,"dt","chib",series="series",mtit=getmtit("XBOX Calls",ckdt),ylab="Sum",addpoints=T,clrs=clrs,
                  vlines2=sdt,backg=xbxback,rotxaxtxt=-30,dfmt="%Y-%m-%d %H:%M %Z",
                  ovsdate=(ckdt$sdate-14*3600),ovedate=(ckdt$edate+14*3600)))
}
```

## SMC Chat and Call Rates

```{r fig.width=14, fig.height=6, echo=T}
stodo <- getstodo()
for (sdt in stodo){
  ckdt <- crackdate(sdt)

  pltdf <- condf %>% gather(series,chib,-dt) %>% filter(series %in% c("rate_winchib","rate_wincall"))
  print(dailyplot(pltdf,"dt","chib",series="series",mtit=getmtit("SMB Chat and Call Rates",ckdt),ylab="Sum",addpoints=T,
                  vlines2=sdt,backg=smcback,rotxaxtxt=-30,dfmt="%Y-%m-%d %H:%M %Z",
                  ovsdate=(ckdt$sdate-14*3600),ovedate=(ckdt$edate+14*3600)))
}
```

## XBox Chat Rates

```{r fig.width=14, fig.height=6, echo=T}
stodo <- getstodo()
clrs <- c("rate_xbxchib"="blue","rate_xtkchib"="darkgreen","rate_xabchib"="purple","rate_xbxchibdiff"="red")

for (sdt in stodo){
  ckdt <- crackdate(sdt)
  pltdf <- condf %>% gather(series,chib,-dt) %>% filter(series %in% c("rate_xbxchib","rate_xtkchib","rate_xabchib","rate_xbxchibdiff"))
  print(dailyplot(pltdf,"dt","chib",series="series",mtit=getmtit("XBOX Chat Rates",ckdt),ylab="Sum",addpoints=T,clrs=clrs,
                  vlines2=sdt,backg=xbxback,rotxaxtxt=-30,dfmt="%Y-%m-%d %H:%M %Z",
                  ovsdate=(ckdt$sdate-14*3600),ovedate=(ckdt$edate+14*3600)))
}
```

# XBox Call Rates

```{r fig.width=14, fig.height=6, echo=T}
stodo <- getstodo()
clrs <- c("rate_xbxcall"="blue","rate_xtkcall"="darkgreen","rate_xabcall"="purple","rate_xbxcalldiff"="red")

for (sdt in stodo){
  ckdt <- crackdate(sdt)
  pltdf <- condf %>% gather(series,chib,-dt) %>% filter(series %in% c("rate_xbxcall","rate_xtkcall","rate_xabcall","rate_xbxcalldiff"))
  print(dailyplot(pltdf,"dt","chib",series="series",mtit=getmtit("XBOX Call Rates",ckdt),ylab="Sum",addpoints=T,clrs=clrs,
                  vlines2=sdt,backg=xbxback,rotxaxtxt=-30,dfmt="%Y-%m-%d %H:%M %Z",
                  ovsdate=(ckdt$sdate-14*3600),ovedate=(ckdt$edate+14*3600)))
}
```

## Done

```{r echo=F}
elap <- as.numeric((Sys.time()-starttime)[1],units="secs")
print(sprintf("%s created on %s took %.1f secs",versionstring,startfmttime,elap))
```