---
title: "Experiements Early 2017 - Read Chat Call Sessions and Merge 0.1"
author: "Mike Wise"
date: "26 April 2017"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Data pre-processed and analyzied from call volume logs and web logs by Marcus Collins. 

Analysis based on R-Scripts from Jacob LaRiviere.

R-Markdown and plots from Mike Wise.

## Library Initialization
```{r, message=F}
library(tidyverse,quietly=T,warn.conflicts=F)
library(lubridate,quietly=T,warn.conflicts=F)
library(scales,quietly=T,warn.conflicts=F)
```

#### Set random seeds, record start time and version.

```{r}
set.seed(1234)
version <-0.1
versionstring <- sprintf("Version %.1f",version)

starttime <- Sys.time()
startfmttime <- sprintf(format(starttime, "%d %b %Y - %H:%M:%S"))

print(sprintf("%s created on %s",versionstring,startfmttime))
```

#### Various constants

```{r}
tztz <- "UTC"  # Apparently all of our time zones are UTC...
firstday <- as.POSIXct("2015-01-01",tz=tztz)  # we will count days from the first day in 2015

smcb1dates <- c("2017-03-08 06:03/blue/100%/2017-03-08 07:57",
                "2017-03-11 08:01/blue/100%/2017-03-11 09:00",
                "2017-03-14 01:02/blue/100%/2017-03-14 03:10",
                "2017-03-15 06:11/blue/100%/2017-03-15 08:24",
                "2017-03-18 08:04/blue/100%/2017-03-18 09:08",
                "2017-03-20 06:04/blue/100%/2017-03-20 08:02")

smcb2dates <- c("2017-04-17 06:00/purple/100%/2017-04-17 08:00",
                "2017-04-17 19:00/purple/100%/2017-04-17 20:00",
                "2017-04-18 01:00/purple/100%/2017-04-18 03:00",
                "2017-04-18 17:00/purple/100%/2017-04-18 18:00",
                "2017-04-19 06:00/purple/100%**/2017-04-19 08:00",
                "2017-04-19 20:00/purple/100%/2017-04-19 21:00",
                "2017-04-20 13:25/purple/100%**/2017-04-20 14:30",
                "2017-04-22 08:00/purple/100%**/2017-04-20 09:00",
                "2017-04-22 18:00/purple/100%**/2017-04-20 19:00",
                "2017-04-23 06:00/purple/100%/2017-04-20 07:00",
                "2017-04-23 19:00/purple/100%/2017-04-20 20:00")

smcb1sdate <- as.POSIXct("2017-03-08",tz=tztz)
smcb1edate <- smcb1sdate+14*24*3600

smcb2sdate <- as.POSIXct("2017-04-17",tz=tztz)
smcb2edate <- smcb2sdate+8*24*3600

smcback <- "lightsteelblue1"
xbxback <- "darkseagreen2"
xabback <- "darkseagreen3"
totback <- "wheat"

fpath <- "TorontoData1"
sdate <- as.POSIXct("2017-03-08",tz=tztz)
edate <- as.POSIXct("2017-04-24",tz=tztz)
```

#### Misc utility functions

```{r}
tzbk <- "US/Pacific"
addStepDateToVek <- function(dates,idx,dtvek,vvek){
  sar1 <- unlist(strsplit(dates[[idx]],"/"))
  datepart1 <- sar1[[1]]
  levpart1 <- sar1[[3]]
  if (!grepl("%",levpart1)){
    # if there is no % don't do anything
    return(vvek)
  }
  dt1 <- as.POSIXct(datepart1,tz=tzbk)
  if (idx<length(dates)){
    sar2 <- unlist(strsplit(dates[[idx+1]],"/"))
    datepart2 <- sar2[[1]]
    dt2 <- as.POSIXct(datepart2,tz=tzbk)
  } else {
    dt2 <- max(dtvek)
  }
  #print(dt1)
  #print(dt2)
  val <- as.numeric(gsub("%","",unlist(strsplit(levpart1,"-"))[[2]]))
  tochg <-  dt1<=dtvek & dtvek<= dt2
  vvek[ tochg ] <- val
  #print(sprintf("changed %d values to %d",sum(tochg),val))
  return(vvek)
}
getStepDates <- function(dates,dtvek){
 vvek <- rep(0,length(dtvek))
 for (i in 1:length(smcdates)){
   vvek <- addStepDateToVek(dates,i,dtvek,vvek)
 }
 return(vvek)
}
getSmcStepDates <- function(dtvek){
 return(getStepDates(smcdates,dtvek))
}
getXabStepDates <- function(dtvek){
 return(getStepDates(xtotdates,dtvek))
}


```


#### Plot Functions

Plots created using ggplot2


```{r}
addVlinesAndText <- function(vlines,gp,hjust=0){
  if (is.null(vlines)) return(gp) # do nothing in this case
  
  # split the lines and convert to data.frame
  sar <- strsplit(vlines,"/")
  # the following reforms the date strings into a data.frame for geom_vline
  ldf <- data.frame(t(matrix(unlist(sar),length(sar[[1]]),length(sar)))) #tricky
  names(ldf) <- c("dt","clr","lab")
  ldf$dt <- as.POSIXct(ldf$dt,tz=tztz)
  ldf$ndt <- as.numeric(ldf$dt)
  # add a newline to the front so as to display the text 
  # this keeps the text from writing on top of the vline
  
  ldf$lab <- paste0("\n",ldf$lab) 
  # now actually add the verticle lines and the text 
  gp <- gp + geom_vline(xintercept=ldf$ndt,color=ldf$clr) +
             annotate(geom="text",x=ldf$dt,y=0,label=ldf$lab,color=ldf$clr,hjust=hjust,angle=90)
  return(gp)
}
addBackground <- function(backg,gp){
  if (is.null(backg)) return(gp) # do nothing in this case
  gp <- gp + theme(panel.background = element_rect(fill = backg))
  return(gp)
}
overdate <- function(ovdate,defdate){
  # date override
  rv <- defdate
  if (!is.null(ovdate)) { 
    rv <- ovdate
  }
  return(rv)
}
dailyplot <- function(ddf,x,y,mtit="",xlab="date",ylab=NULL,vlines=NULL,backg=NULL,series=NULL,clrs=NULL,
                      hjust=0,rotxaxtxt=0,ovsdate=NULL,ovedate=NULL){
  # Single series plot  with monthly breaks on the x-axis
  
  # override dates if needed
  dpsdate <- overdate(ovsdate,sdate)
  dpedate <- overdate(ovedate,edate)
  
  gp <- ggplot(ddf,aes_string(x=x,y=y)) + 
             geom_line(aes_string(color=series),na.rm=T)  +
             xlab(xlab) + ylab(ylab) + ggtitle(mtit) +
             scale_x_datetime("Date",breaks = date_breaks("1 days"),limits=c(dpsdate,dpedate))

  if (!is.null(clrs)){
    gp <- gp + scale_color_manual(values=clrs)
  }
  gp <- addVlinesAndText(vlines,gp,hjust=hjust)

  gp <- addBackground(backg,gp)
  
  if (rotxaxtxt!=0){
    gp <- gp + theme(axis.text.x = element_text(angle = rotxaxtxt, hjust = 0))
  }

  return(gp)
}
```

## Read in chat volume data 

```{r}
chstload <- Sys.time()
readChatVolume <- function(frdate,todate,fname){
  fstload <- Sys.time()
  cfname <- sprintf("%s/%s",fpath,fname)
  lcdf <- read.csv(cfname)
  print(sprintf("read %s - read rows:%d  cols:%d",cfname,nrow(lcdf),ncol(lcdf)))
  
  
  lcdf$dt<- as.POSIXct(lcdf$DateHour,format="%m/%d/%Y %I:%M:%S %p",tz=tztz)
  
  #filter early
  n1 <- nrow(lcdf)
  lcdf <- lcdf %>% filter( frdate<=dt & dt<todate)
  n2 <- nrow(lcdf)
  dtd<- as.POSIXct(lcdf$DateHour,format="%m/%d/%Y",tz=tztz)

 # lcdf$temp_date<- as.POSIXct(lcdf$Date,format="%m/%d/%Y %I:%M:%S %p",tz=tztz)
  lcdf  <- lcdf %>% mutate( dnum = round(as.numeric(difftime(dtd,firstday,units="days")))) %>%
                    mutate( hnum = dnum*24 + hour(dt))
    
  # restrict rows as different files sometimes have extra colums
  lcdf <- lcdf %>% arrange( dt ) # sort
  lcdf <- lcdf[,c("dt","dnum","hnum","IsSXC","IsSMC","IsAB",
                  "Market","AvgChatDuration","AvgEstWaitTime","ChatsInBlock")]
  elap <- as.numeric((Sys.time()-fstload)[1],units="secs")
  
  lcdf <- lcdf %>% filter( Market=="en-us" ) %>% arrange( dt )
#  lcdf <- lcdf %>% mutate( IsAB=grepl("^A&B",Subject)) %>%
#                   mutate( IsTk=grepl("^TS",Subject))
  
  # just need these columns and group by hour
  print(names(lcdf))
  lcdf <- lcdf[,c("dt","dnum","hnum","IsSMC","IsAB","ChatsInBlock")]
  lcdf <- lcdf %>% group_by(hnum) %>%
                   summarize(dt=min(dt),dnum=min(dnum),
                             totchib=sum(ChatsInBlock),
                             winchib=sum((IsSMC=="True")*ChatsInBlock),
                             xbxchib=sum((IsSMC=="False")*ChatsInBlock),
                             xabchib=sum((IsSMC=="False")*(IsAB=="True")*ChatsInBlock),
                             xtkchib=sum((IsSMC=="False")*(IsAB=="False")*ChatsInBlock)
                             ) %>%
                   mutate(ChatsInBlock=NULL,IsSMC=NULL) %>%
                   arrange(hnum)

  print(sprintf("Read %d of %d lines from %s in %.1f secs",n2,n1,cfname,elap))
  return(lcdf)
}
chdf <- readChatVolume(sdate,edate,"chat_vol_duration_from_SKPI_2017.csv")

chdf <- chdf %>% arrange(hnum)

chelap <- as.numeric((Sys.time()-chstload)[1],units="secs")
print(sprintf("Loading chat data took %.1f secs",chelap))
```
## Total chat volume plots

```{r fig.width=14, fig.height=6, echo=T}

ecdf <- chdf %>% group_by(hnum) %>% 
                 summarise(dt=min(dt),
                           Total=sum(totchib),Windows=sum(winchib),Xbox=sum(xbxchib)) %>%
                 mutate( hnum=NULL ) %>% # delete dnum col
                 gather(series,chats,-dt)

dailyplot(ecdf,"dt","chats",series="series",mtit="Total Chats - Week1",ylab="Chat Count",
          vlines=smcb1dates,backg=totback,rotxaxtxt=0,
          ovsdate=smcb1sdate,ovedate=smcb1edate)
```
```{r fig.width=14, fig.height=6, echo=T}
dailyplot(ecdf,"dt","chats",series="series",mtit="Total Chats - Week2",ylab="Chat Count",
          vlines=smcb2dates,backg=totback,rotxaxtxt=0,
          ovsdate=smcb2sdate,ovedate=smcb2edate)
```

## Xbox chat volume plots

```{r fig.width=14, fig.height=6, echo=T}

ecdf <- chdf %>% group_by(hnum) %>% 
                 summarise(dt=min(dt),
                           xbox_total=sum(xbxchib),
                           xbox_tech=sum(xtkchib),xbox_ab=sum(xabchib),
                           xbox_diff=sum(xabchib)-sum(xtkchib)) %>%
                 mutate( hnum=NULL ) %>% # delete dnum col
                 gather(series,chats,-dt)
clrs <- c("xbox_total"="blue","xbox_tech"="darkgreen","xbox_ab"="purple","xbox_diff"="red")

dailyplot(ecdf,"dt","chats",series="series",mtit="Xbox Chat Breakdown by Tech/AB - Week 1",ylab="Chat Count",
          vlines=smcb1dates,backg=xbxback,clrs=clrs,hjust=0.5,
          ovsdate=smcb1sdate,ovedate=smcb1edate)
```

```{r fig.width=14, fig.height=6, echo=T}

ecdf <- ecdf %>% filter(series=="xbox_diff")

dailyplot(ecdf,"dt","chats",series="series",mtit="Xbox Chat Breakdown by Tech/AB - Week 1",ylab="Chat Count",
          vlines=smcb1dates,backg=xbxback,clrs=clrs,hjust=0.5,
          ovsdate=smcb1sdate,ovedate=smcb1edate)
```

```{r fig.width=14, fig.height=6, echo=T}

ecdf <- chdf %>% group_by(hnum) %>% 
                 summarise(dt=min(dt),
                           xbox_total=sum(xbxchib),
                           xbox_tech=sum(xtkchib),xbox_ab=sum(xabchib),
                           xbox_diff=sum(xabchib)-sum(xtkchib)) %>%
                 mutate( hnum=NULL ) %>% # delete dnum col
                 gather(series,chats,-dt)
clrs <- c("xbox_total"="blue","xbox_tech"="darkgreen","xbox_ab"="purple","xbox_diff"="red")


dailyplot(ecdf,"dt","chats",series="series",mtit="Xbox Chat Breakdown by Tech/AB - Week 2",ylab="Chat Count",
          vlines=smcb2dates,backg=xbxback,clrs=clrs,hjust=0.5,
          ovsdate=smcb2sdate,ovedate=smcb2edate)
```

```{r fig.width=14, fig.height=6, echo=T}

ecdf <- ecdf %>% filter(series=="xbox_diff")

dailyplot(ecdf,"dt","chats",series="series",mtit="Xbox Chat Breakdown by Tech/AB - Week 2",ylab="Chat Count",
          vlines=smcb2dates,backg=xbxback,clrs=clrs,hjust=0.5,
          ovsdate=smcb2sdate,ovedate=smcb2edate)
```

## Read in call volume data

```{r}
clstload <- Sys.time()
readCallVolume <- function(frdate,todate,fname){
  cfname <- sprintf("%s/%s",fpath,fname)
  lcdf <- read.csv(cfname)
  print(sprintf("read %s - read rows:%d  cols:%d",cfname,nrow(lcdf),ncol(lcdf)))

  dtd<- as.POSIXct(lcdf$Date,format="%m/%d/%Y",tz=tztz)

  lcdf  <- lcdf %>% mutate( dt = as.POSIXct(lcdf$DateHour,format="%m/%d/%Y %I:%M:%S %p",tz=tztz)) %>%
                    mutate( dnum = round(as.numeric(difftime(dtd,firstday,units="days")))) %>%
                    mutate( hnum = dnum*24 + hour(dt)) %>%
                    arrange( dt ) # sort

  n1 <- nrow(lcdf)
  lcdf <- lcdf %>% filter( frdate<=dt & dt<todate)
  n2 <- nrow(lcdf)
  print(sprintf("Read %d of %d lines from %s",n2,n1,cfname))
  lcdf <- lcdf %>% filter( COUNTRY_NAME=="United States" ) %>% arrange( dt )
  print(sprintf("Rows after filtering to United States only: %d",nrow(lcdf)))
  
  # just need these columns
  lcdf <- lcdf[,c("dt","dnum","hnum","WindowsCalls","XboxTotalCalls","XboxABCalls")]
  
  # group by hour (this should actually do nothing, but just in case)
  lcdf <- lcdf %>% group_by(hnum) %>% 
                   summarise(dt=min(dt),
                             dnum=min(dnum),
                             wincall=sum(WindowsCalls),
                             xtkcall=sum(XboxTotalCalls),
                             xabcall=sum(XboxABCalls),
                             xbxcall=sum(XboxTotalCalls+XboxABCalls)) %>%
                   mutate(totcall=wincall+xbxcall)
  return(lcdf)
}
cldf <- readCallVolume(sdate,edate,"genesys_ivr_call_data.csv")

clelap <- as.numeric((Sys.time()-clstload)[1],units="secs")
print(sprintf("Loading call data took %.1f secs",clelap))
```


## Total call volume plots

```{r fig.width=14, fig.height=6, echo=T}

ecdf <- cldf %>% group_by(hnum) %>% 
                 summarise(dt=min(dt),Total=sum(wincall+xbxcall),Windows=sum(wincall),Xbox=sum(xbxcall)) %>%
                 mutate( hnum=NULL ) %>% # delete dnum col
                 gather(series,calls,-dt)

dailyplot(ecdf,"dt","calls",series="series",mtit="Total Call Volumne - Week 1",ylab="Call Count",
          vlines=smcb1dates,backg=totback,rotxaxtxt=0,
          ovsdate=smcb1sdate,ovedate=smcb1edate)
```
```{r fig.width=14, fig.height=6, echo=T}

dailyplot(ecdf,"dt","calls",series="series",mtit="Total Call Volumne - Week 2",ylab="Call Count",
          vlines=smcb2dates,backg=totback,rotxaxtxt=0,
          ovsdate=smcb2sdate,ovedate=smcb2edate)
```

## Xbox call volume plots

```{r fig.width=14, fig.height=8, echo=T}

ecdf <- cldf %>% group_by(hnum) %>% 
                 summarise(dt=min(dt),xbox_total=sum(xtkcall+xabcall),
                                      xbox_tech=sum(xtkcall),xbox_ab=sum(xabcall),
                                      xbox_diff=sum(xabcall)-sum(xtkcall)) %>%
                 mutate( hnum=NULL ) %>% # delete dnum col
                 gather(series,calls,-dt)

clrs <- c("xbox_total"="blue","xbox_tech"="darkgreen","xbox_ab"="purple","xbox_diff"="red")


dailyplot(ecdf,"dt","calls",series="series",mtit="Xbox Call Breakdown by Tech/AB - Week 1",ylab="Call Count",
          vlines=smcb1dates,backg=xbxback,clrs=clrs,hjust=0.5,
          ovsdate=smcb1sdate,ovedate=smcb1edate)
```


```{r fig.width=14, fig.height=6, echo=T}
ecdf <- ecdf %>% filter(series=="xbox_diff")

dailyplot(ecdf,"dt","calls",series="series",mtit="Xbox Call Breakdown by Tech/AB - Week 1",ylab="Call Count",
          vlines=smcb1dates,backg=xbxback,clrs=clrs,hjust=0.5,
          ovsdate=smcb1sdate,ovedate=smcb1edate)
```

```{r fig.width=14, fig.height=8, echo=T}

ecdf <- cldf %>% group_by(hnum) %>% 
                 summarise(dt=min(dt),xbox_total=sum(xtkcall+xabcall),
                                      xbox_tech=sum(xtkcall),xbox_ab=sum(xabcall),
                                      xbox_diff=sum(xabcall)-sum(xtkcall)) %>%
                 mutate( hnum=NULL ) %>% # delete dnum col
                 gather(series,calls,-dt)

clrs <- c("xbox_total"="blue","xbox_tech"="darkgreen","xbox_ab"="purple","xbox_diff"="red")


dailyplot(ecdf,"dt","calls",series="series",mtit="Xbox Call Breakdown by Tech/AB - Week 2",ylab="Call Count",
          vlines=smcb2dates,backg=xbxback,clrs=clrs,hjust=0.5,
          ovsdate=smcb2sdate,ovedate=smcb2edate)
```

```{r fig.width=14, fig.height=6, echo=T}
ecdf <- ecdf %>% filter(series=="xbox_diff")

dailyplot(ecdf,"dt","calls",series="series",mtit="Xbox Call Breakdown by Tech/AB - Week 2",ylab="Call Count",
          vlines=smcb2dates,backg=xbxback,clrs=clrs,hjust=0.5,
          ovsdate=smcb2sdate,ovedate=smcb2edate)
```

## Read in SMC Active User/Session data

```{r}
ssstload <- Sys.time()
readSessionVolume <- function(frdate,todate,fname){
  sfname <- sprintf("%s/%s",fpath,fname)
  svdf <- read.csv(sfname)  
  print(sprintf("read %s - read rows:%d  cols:%d",sfname,nrow(svdf),ncol(svdf)))

  temp_dstr   <- sprintf("%d-%2.2d-%2.2d %2.2d",
                         svdf$EventUtcYear,svdf$EventUtcMonth,
                         svdf$EventUtcDay,svdf$EventUtcHour)
  
  dtd   <- as.POSIXct(temp_dstr,format="%Y-%m-%d",tz=tztz)

  svdf <- svdf %>% mutate( dt=as.POSIXct(temp_dstr,format="%Y-%m-%d %H",tz="UTC") ) %>%
                   mutate( dnum=round(as.numeric(difftime(dtd,firstday,units="days"))) ) %>%
                   mutate( hnum  = dnum*24 + hour(dt) )

  n1 <- nrow(svdf)
  svdf <- svdf %>% filter( frdate<=dt & dt<todate)
  n2 <- nrow(svdf)
  svdf$actsess <- svdf$HourlyActiveSessions
  svdf$actuser <- svdf$HourlyActiveUsers
  svdf <- svdf[,c("hnum","dt","dnum","actsess","actuser")]
  print(sprintf("Read %d of %d lines from %s",n2,n1,sfname))
  return(svdf)
}
svdf <- readSessionVolume(sdate,edate,"hourly-smc-traffic-2017.csv")

svdf <- svdf %>% arrange(dt)                              # sort
# svdf <- svdf %>% filter( HourlyActiveSessions>1000 )   # plausiblity check mitigates range overflow in following plots


print(sprintf("Total SessionVolume rows:%d",nrow(svdf)))
sselap <- as.numeric((Sys.time()-ssstload)[1],units="secs")
print(sprintf("Loading Session data took %.1f secs",sselap))
```


# Merge 
```{r echo=T}
cccc <- inner_join(chdf,cldf,by="hnum",suffix=c(".chat",".call"))
print(sprintf("call-chat join merged %d x %d rows to %d rows",nrow(chdf),nrow(cldf),nrow(cccc)))

print(sprintf("dt   mismatches:%d",sum(cccc$dt.chat!=cccc$dt.call)))
print(sprintf("dnum mismatches:%d",sum(cccc$dnum.chat!=cccc$dnum.call)))

tdf <- inner_join(cccc,svdf,by="hnum",suffix=c(".cccc",".sess"))
print(sprintf("cccc-sess join merged %d x %d rows to %d rows",nrow(cccc),nrow(svdf),nrow(tdf)))

print(sprintf("dt   mismatches:%d",sum(tdf$dt.chat!=tdf$dt)))
print(sprintf("dnum mismatches:%d",sum(tdf$dnum.chat!=tdf$dnum)))
```

# Re-order the columns and then Write it out
```{r echo=T}
condf <- tdf[,c("dt","dnum","hnum","totchib","winchib","xbxchib","xtkchib","xabchib",
                                   "totcall","wincall","xbxcall","xtkcall","xabcall",
                                   "actsess","actuser")]
tfname <- sprintf("%s/%s",fpath,"colsolidatedEarly2017TorontoData01.csv")
write.csv(tdf,tfname)
print(sprintf("Wrote %d rows and %d cols to %s",nrow(tdf),ncol(tdf),tfname))
```


## Done

```{r echo=F}
elap <- as.numeric((Sys.time()-starttime)[1],units="secs")
print(sprintf("%s created on %s took %.1f secs",versionstring,startfmttime,elap))
```