---
title: "Many Regressions"
author: "Mike Wise"
date: "17 Mar 2017"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Data pre-processed and analyzied from chat logs and web logs by Marcus Collins. 

Analysis based on R-Scripts from Jacob LaRiviere.

R-Markdown and plots from Mike Wise.

## Initialization of libraries
```{r, message=F}
library(tidyverse,quietly=T,warn.conflicts=F)
library(lubridate,quietly=T,warn.conflicts=F)
library(scales,quietly=T,warn.conflicts=F)
library(zoo,quietly=T,warn.conflicts=F)
library(lmtest,quietly=T,warn.conflicts=F)
library(sandwich,quietly=T,warn.conflicts=F)
library(gridExtra)
```

Set random seeds, record start time and version.

```{r}
set.seed(1234)
version <-0.1
versionstring <- sprintf("Version %.1f",version)

starttime <- Sys.time()
startfmttime <- sprintf(format(starttime, "%d %b %Y - %H:%M:%S"))

print(sprintf("%s created on %s",versionstring,startfmttime))
```


#### Various constants

```{r}
tztz <- "UTC"  # Apparently all of our time zones are UTC...
s2date <- function(strdate){
  return(as.POSIXct(strdate,tz=tztz))
}
firstday <- s2date("2015-01-01")  # we will count days from the first day in 2015

smcdates <- c("2016-08-17/red/0-30%","2016-09-1/red/30-50%","2016-09-07/red/50-100%")
xtotdates <- c("2016-10-11/purple/0-10%","2016-10-18/purple/10-30%","2016-11-01/purple/30-50%","2016-12-15/purple/50-90%",
              "2016-11-17/blue/content change")
totdates <- c(smcdates,xtotdates)
smcback <- "lightsteelblue1"
xbxback <- "darkseagreen2"
xabback <- "darkseagreen3"
totback <- "wheat"

fpath <- "../TorontoData"
sdate <- s2date("2016-06-01")
mdate <- s2date("2017-01-01")
edate <- s2date("2017-03-07")
verbose <- 1
```

#### Misc utility functions

```{r}

addStepDateToVek <- function(dates,idx,dtvek,vvek){
  sar1 <- unlist(strsplit(dates[[idx]],"/"))
  datepart1 <- sar1[[1]]
  levpart1 <- sar1[[3]]
  if (!grepl("%",levpart1)){
    # if there is no % don't do anything
    return(vvek)
  }
  dt1 <- s2date(datepart)
  if (idx<length(dates)){
    sar2 <- unlist(strsplit(dates[[idx+1]],"/"))
    datepart2 <- sar2[[1]]
    dt2 <- s2date(datepart2)
  } else {
    dt2 <- max(dtvek)
  }
  #print(dt1)
  #print(dt2)
  val <- as.numeric(gsub("%","",unlist(strsplit(levpart1,"-"))[[2]]))
  tochg <-  dt1<=dtvek & dtvek<= dt2
  vvek[ tochg ] <- val
  #print(sprintf("changed %d values to %d",sum(tochg),val))
  return(vvek)
}
getStepDates <- function(dates,dtvek){
 vvek <- rep(0,length(dtvek))
 for (i in 1:length(smcdates)){
   vvek <- addStepDateToVek(dates,i,dtvek,vvek)
 }
 return(vvek)
}
getSmcStepDates <- function(dtvek){
 return(getStepDates(smcdates,dtvek))
}
getXabStepDates <- function(dtvek){
 return(getStepDates(xtotdates,dtvek))
}
```



#### Plot functions


```{r}
addVlinesAndText <- function(vlines,gp){
  if (is.null(vlines)) return(gp) # do nothing in this case
  
  # split the lines and convert to data.frame
  sar <- strsplit(vlines,"/")
  # the following reforms the date strings into a data.frame for geom_vline
  ldf <- data.frame(t(matrix(unlist(sar),length(sar[[1]]),length(sar)))) #tricky
  names(ldf) <- c("dt","clr","lab")
  ldf$dt <- s2date(ldf$dt)
  ldf$ndt <- as.numeric(ldf$dt)
  # add a newline to the front so as to display the text 
  # this keeps the text from writing on top of the vline
  
  ldf$lab <- paste0("\n",ldf$lab) 
  # now actually add the verticle lines and the text 
  gp <- gp + geom_vline(xintercept=ldf$ndt,color=ldf$clr) +
             annotate(geom="text",x=ldf$dt,y=0,label=ldf$lab,color=ldf$clr,hjust=0,angle=90,na.rm=T)
  return(gp)
}
addBackground <- function(backg,gp){
  if (is.null(backg)) return(gp) # do nothing in this case
  gp <- gp + theme(panel.background = element_rect(fill = backg))
  return(gp)
}
overdate <- function(ovdate,defdate){
  # date override
  rv <- defdate
  if (!is.null(ovdate)) { 
    rv <- ovdate
  }
  return(rv)
}
dailyplot <- function(ddf,x,y,mtit="",xlab="date",ylab=NULL,vlines=NULL,backg=NULL,series=NULL,ovsdate=NULL,ovedate=NULL){
  # Single series plot  with monthly breaks on the x-axis
  
  # override dates if needed
  dpsdate <- overdate(ovsdate,sdate)
  dpedate <- overdate(ovedate,edate)
  
  brkctrl <- "1 month"
  dltdays <- difftime(dpedate,dpsdate,"days") 
  if (dltdays<30) brkctrl <- "1 day"
  
  gp <- ggplot(ddf,aes_string(x=x,y=y)) + 
             geom_line(aes_string(color=series),na.rm=T)  +
             xlab(xlab) + ylab(ylab) + ggtitle(mtit) +
             scale_x_datetime("Date",breaks = date_breaks(brkctrl),limits=c(dpsdate,dpedate))

  gp <- addVlinesAndText(vlines,gp)

  gp <- addBackground(backg,gp)

  return(gp)
}
residplot <- function(ddf,x,y,mtit="",xlab="date",ylab=NULL,vlines=NULL,backg=NULL,series=NULL,ovsdate=NULL,ovedate=NULL){
  # Single series plot  with monthly breaks on the x-axis
  
  # override dates if needed
  dpsdate <- overdate(ovsdate,sdate)
  dpedate <- overdate(ovedate,edate)
  
  brkctrl <- "1 month"
  dltdays <- difftime(dpedate,dpsdate,"days") 
  if (dltdays<30) brkctrl <- "1 day"
  
  gp <- ggplot(ddf,aes_string(x=x,y=y)) + 
             geom_point(aes_string(color=series),na.rm=T)  +
             xlab(xlab) + ylab(ylab) + ggtitle(mtit) +
             scale_x_datetime("Date",breaks = date_breaks(brkctrl),limits=c(dpsdate,dpedate))

  gp <- addVlinesAndText(vlines,gp)

  gp <- addBackground(backg,gp)
  
  hp <- ggplot(ddf) + geom_histogram(aes_string(x=y),binwidth=10)
  hp <- addBackground(backg,hp)
  
  ghp <- grid.arrange(gp, hp, ncol=2,widths = c(2,1))

  return(ghp)
}
```

## Read in consolidated chat, call, and session volume data

```{r}
stload <- Sys.time()
tfname <- sprintf("%s/%s",fpath,"colsolidatedTorontoData01.csv")
condf <- read.csv(tfname)
condf$dt <- as.POSIXct(condf$dt,tz=tztz)

dcondf <- condf %>% group_by(dnum) %>% summarise(dt=min(dt),
                                                 totchib=sum(totchib),winchib=sum(winchib),xbxchib=sum(xbxchib),
                                                 totcall=sum(totcall),wincall=sum(wincall),xbxcall=sum(xbxcall),
                                                 actsess=sum(actsess),actuser=sum(actuser)
                                                 )

elap <- as.numeric((Sys.time()-stload)[1],units="secs")
print(sprintf("Loading consolidated data took %.1f secs",elap))
```


# chats

```{r fig.width=14, fig.height=6, echo=T}
if (verbose>=2){
  pltdf <- dcondf %>% gather(series,chib,-dt) %>% filter(series %in% c("totchib","winchib","xbxchib"))
  dailyplot(pltdf,"dt","chib",series="series",mtit="Chats In Block",ylab="Sum",vlines=totdates,backg=totback)
}
````

```{r fig.width=14, fig.height=6, echo=T}
if (verbose>=2){
  pltdf <- dcondf %>% gather(series,call,-dt) %>% filter(series %in% c("totcall","wincall","xbxcall"))
  dailyplot(pltdf,"dt","call",series="series",mtit="Calls",ylab="Sum",vlines=totdates,backg=totback)
}
```


```{r fig.width=14, fig.height=6, echo=T}
if (verbose>=2){
  pltdf <- dcondf %>% gather(series,active,-dt) %>% filter(series %in% c("actsess","actuser"))
  dailyplot(pltdf,"dt","active",series="series",mtit="Sessions",ylab="Sum",vlines=totdates,backg=totback)
}
```

## SMC daily plots
```{r fig.width=14, fig.height=6, echo=T}
crackdate <- function(datestr){
  sar <- unlist(strsplit(datestr,"/"))
  date <- s2date(sar[[1]])
  val <- 0
  sval <- ""
  levpart <- sar[[3]]
  if (grepl("%",levpart)){
    levpart <- gsub("%","",levpart)
    val <- as.numeric(unlist(strsplit(levpart,"-"))[[2]])
    sval <- gsub("-","_",levpart)
  }
  return(list(date=date,val=val,sval=sval))
}
getregdf <- function(df,vname,discdate,befdays,aftdays,dates){
  
  # filter on time
  sregdate <- discdate - days(befdays)
  eregdate <- discdate + days(aftdays)
  df <- df %>% filter( sregdate <= dt & dt <= eregdate) 
  
  df <- df %>% mutate( hour=as.factor(hour(dt)) ) %>%
               mutate( idx=1:nrow(df) ) 

  # add level variables
  cutidx <- which(df$dt==discdate)

    df <- df %>% mutate( lin1=if_else(idx<cutidx,idx,0L)) %>%
                 mutate( lin2=if_else(idx<cutidx,0L,idx-cutidx+1L)) %>%
                 mutate( pastbrk=if_else(idx<cutidx,0L,1L) )

  # skydates
  for (strdate in dates){
    crk <- crackdate(strdate)
    skyname <- paste0("sky",crk$sval)
    df[[skyname]] <- ifelse(df$dt<crk$date,0,1)
  }
  return(df)
}
doregression <- function(df,vname,discdatecrk,befdays,aftdays,dates){
  df <- getregdf(df,vname,discdatecrk,befdays,aftdays,dates)
  formstr <- sprintf("%s ~ hour + lin1 + lin2 + pastbrk",vname)
  form <- as.formula(formstr)
  fit <- glm(form,data=df)
  print(summary(fit))
  print(coeftest(fit, vcov = vcovHC(fit, "HC1")))
  df$resid <- resid(fit)
  df$predicted <-  df[[vname]]-df$resid
  return(list(df=df,formstr=formstr))
}
regress <- function(df,vname,cutdate,befdays,aftdays,dates){
}
```




```{r fig.width=14, fig.height=6, echo=T}
#hsmcdf <- condf %>% group_by(hnum) %>% summarize(dt=min(dt),cib = sum(ChatsInBlock))
cutdate <- smcdates[1]
discdate <- crackdate(cutdate)$date
vname <- "winchib"
rv <- doregression(condf,vname,discdate,7,7,cutdate)
df1 <- rv$df %>%  gather_("series",vname,c(vname,"predicted"))
mtit <- sprintf("SSMC - Hourly Chats In Block - %s",rv$formstr)
dailyplot(df1,"dt",vname,series="series",mtit,ylab="Sum",vlines=smcdates,backg=smcback,ovsdate=min(df1$dt),ovedate=max(df1$dt))
```
```{r fig.width=14, fig.height=6, echo=T}
mtit <- sprintf("SSMC - Hourly Chats In Block - Residuals - %s",rv$formstr)
residplot(df1,"dt","resid",mtit,ylab="Sum",vlines=smcdates,backg=smcback,ovsdate=min(df1$dt),ovedate=max(df1$dt))
```


```{r fig.width=14, fig.height=6, echo=T}
cutdate <- smcdates[2]
discdate <- crackdate(cutdate)$date
vname <- "winchib"
rv <- doregression(condf,vname,discdate,7,7,cutdate)
df1 <- rv$df %>%  gather_("series",vname,c(vname,"predicted"))
mtit <- sprintf("SSMC - Hourly Chats In Block - %s",rv$formstr)
dailyplot(df1,"dt",vname,series="series",mtit,ylab="Sum",vlines=smcdates,backg=smcback,ovsdate=min(df1$dt),ovedate=max(df1$dt))

```
```{r fig.width=14, fig.height=6, echo=T}
mtit <- sprintf("SSMC - Hourly Chats In Block - Residuals - %s",rv$formstr)
residplot(df1,"dt","resid",mtit,ylab="Sum",vlines=smcdates,backg=smcback,ovsdate=min(df1$dt),ovedate=max(df1$dt))
```
```{r fig.width=14, fig.height=6, echo=T}
cutdate <- smcdates[3]
discdate <- crackdate(cutdate)$date
vname <- "winchib"
rv <- doregression(condf,vname,discdate,7,7,cutdate)
df1 <- rv$df %>%  gather_("series",vname,c(vname,"predicted"))
mtit <- sprintf("SSMC - Hourly Chats In Block - %s",rv$formstr)
dailyplot(df1,"dt",vname,series="series",mtit,ylab="Sum",vlines=smcdates,backg=smcback,ovsdate=min(df1$dt),ovedate=max(df1$dt))
```
```{r fig.width=14, fig.height=6, echo=T}
mtit <- sprintf("SSMC - Hourly Chats In Block - Residuals - %s",rv$formstr)
residplot(df1,"dt","resid",mtit,ylab="Sum",vlines=smcdates,backg=smcback,ovsdate=min(df1$dt),ovedate=max(df1$dt))
```

## Done
```{r echo=F}
elap <- as.numeric((Sys.time()-starttime)[1],units="secs")
print(sprintf("%s created on %s took %.1f secs",versionstring,startfmttime,elap))
```