---
title: "Model1 Regressions - V06"
author: "Mike Wise"
date: "27 Mar 2017"
output: html_document
---
<STYLE TYPE="text/css">
<!--
  td{
    font-family: Arial; 
    font-size: 7pt;
    padding:1px;
    cellpadding="2";
    cellspacing="2"
  }
  th {
    font-family: Arial; 
    font-size: 7pt;
    height: 20px;
    font-weight: bold;
    text-align: right;
    background-color: #ccccff;
  }
  table { 
    border-spacing: 420x;
    border-collapse: collapse;
  }
--->
</STYLE>

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Data pre-processed and analyzed from chat logs and web logs by Marcus Collins. 

Analysis based on R-Scripts from Jacob LaRiviere.

Experiment designs from Marcus Collins and Jacob LaRiveier.

R-Markdown and plots from Mike Wise.

## Initialization of libraries
```{r, message=F}
library(tidyverse,quietly=T,warn.conflicts=F)
library(lubridate,quietly=T,warn.conflicts=F)
library(scales,quietly=T,warn.conflicts=F)
library(zoo,quietly=T,warn.conflicts=F)
library(lmtest,quietly=T,warn.conflicts=F)
library(sandwich,quietly=T,warn.conflicts=F)
library(gridExtra,quietly=T,warn.conflicts = F)
library(knitr,quietly=T,warn.conflicts = F)
```

Set random seeds, record start time and version.

```{r}
set.seed(1234)
version <-0.4
versionstring <- sprintf("Version %.1f",version)

starttime <- Sys.time()
startfmttime <- sprintf(format(starttime, "%d %b %Y - %H:%M:%S"))

print(sprintf("%s created on %s",versionstring,startfmttime))
```


#### Various constants

```{r}
tztz <- "UTC"  # Apparently all of our time zones are UTC...
s2date <- function(strdate){
  return(as.POSIXct(strdate,tz=tztz))
}
firstday <- s2date("2015-01-01")  # we will count days from the first day in 2015

smcdates <- c("2016-08-17/red/0-30%","2016-09-1/red/30-50%","2016-09-07/red/50-100%")
xbxdates <- c("2016-10-11/purple/0-10%","2016-10-18/purple/10-30%","2016-11-01/purple/30-50%","2016-12-15/purple/50-90%",
              "2016-11-17/blue/content change")
totdates <- c(smcdates,xbxdates)
smcback <- "lightsteelblue1"
xbxback <- "darkseagreen2"
xabback <- "darkseagreen3"
totback <- "wheat"

fpath <- "../TorontoData"
sdate <- s2date("2016-06-01")
mdate <- s2date("2017-01-01")
edate <- s2date("2017-03-07")
verbose <- 2
justdoone <- F # for testing
```

#### Misc utility functions

```{r}
crackdate <- function(datestr){
  sar <- unlist(strsplit(datestr,"/"))
  sdate <- sar[[1]]
  date <- s2date(sdate)
  val <- 0
  sval <- sar[[3]]
  levpart <- sar[[3]]
  pctpresent <- F
  if (grepl("%",levpart)){
    levpart <- gsub("%","",levpart)
    val <- as.numeric(unlist(strsplit(levpart,"-"))[[2]])
    sval <- gsub("-","_",levpart)
    pctpresent <- T
  }
  return(list(date=date,sdate=sdate,val=val,sval=sval,pctpresent=pctpresent))
}

addStepDateToVek <- function(dates,idx,dtvek,vvek){
  cd1 <- crackdate(dates[[idx]])
  if (!cd1$pctpresent){
    # if there is no % don't do anything
    return(vvek)
  }
  dt1 <- cd1$date
  if (idx<length(dates)){
    cd2 <- crackdate(dates[[idx+1]])
    dt2 <- cd2$date
  } else {
    dt2 <- max(dtvek)
  }
  #print("addstepdate")
  #print(dt1)
  #print(dt2)
  val <- cd1$val
  tochg <-  dt1<=dtvek & dtvek<= dt2
  vvek[ tochg ] <- val
  #print(sprintf("changed %d values to %d",sum(tochg),val))
  return(vvek)
}
getStepDates <- function(dates,dtvek){
 vvek <- rep(0,length(dtvek))
 for (i in 1:length(dates)){
   vvek <- addStepDateToVek(dates,i,dtvek,vvek)
 }
 return(vvek)
}
getSmcStepDates <- function(dtvek){
 return(getStepDates(smcdates,dtvek))
}
getXabStepDates <- function(dtvek){
 return(getStepDates(xbxdates,dtvek))
}
```



#### Plot functions


```{r}
addVlinesAndText <- function(vlines,gp){
  if (is.null(vlines)) return(gp) # do nothing in this case
  
  # split the lines and convert to data.frame
  sar <- strsplit(vlines,"/")
  # the following reforms the date strings into a data.frame for geom_vline
  ldf <- data.frame(t(matrix(unlist(sar),length(sar[[1]]),length(sar)))) #tricky
  names(ldf) <- c("dt","clr","lab")
  ldf$dt <- s2date(ldf$dt)
  ldf$ndt <- as.numeric(ldf$dt)
  # add a newline to the front so as to display the text 
  # this keeps the text from writing on top of the vline
  
  ldf$lab <- paste0("\n",ldf$lab) 
  # now actually add the verticle lines and the text 
  gp <- gp + geom_vline(xintercept=ldf$ndt,color=ldf$clr) +
             annotate(geom="text",x=ldf$dt,y=0,label=ldf$lab,color=ldf$clr,hjust=0,angle=90,na.rm=T)
  return(gp)
}
addBackground <- function(backg,gp){
  if (is.null(backg)) return(gp) # do nothing in this case
  gp <- gp + theme(panel.background = element_rect(fill = backg))
  return(gp)
}
overdate <- function(ovdate,defdate){
  # date override
  rv <- defdate
  if (!is.null(ovdate)) { 
    rv <- ovdate
  }
  return(rv)
}
dailyplot <- function(ddf,x,y,mtit="",xlab="date",ylab=NULL,vlines=NULL,backg=NULL,series=NULL,ovsdate=NULL,ovedate=NULL){
  # Single series plot  with monthly breaks on the x-axis
  
  # override dates if needed
  dpsdate <- overdate(ovsdate,sdate)
  dpedate <- overdate(ovedate,edate)
  
  brkctrl <- "1 month"
  dltdays <- difftime(dpedate,dpsdate,"days") 
  if (dltdays<30) brkctrl <- "1 day"
  
  gp <- ggplot(ddf,aes_string(x=x,y=y)) + 
             geom_line(aes_string(color=series),na.rm=T)  +
             xlab(xlab) + ylab(ylab) + ggtitle(mtit) +
             scale_x_datetime("Date",breaks = date_breaks(brkctrl),limits=c(dpsdate,dpedate))

  gp <- addVlinesAndText(vlines,gp)

  gp <- addBackground(backg,gp)

  return(gp)
}
residplot <- function(ddf,x,y,mtit="",xlab="date",ylab=NULL,vlines=NULL,backg=NULL,series=NULL,ovsdate=NULL,ovedate=NULL){
  # Single series plot  with monthly breaks on the x-axis
  
  # override dates if needed
  dpsdate <- overdate(ovsdate,sdate)
  dpedate <- overdate(ovedate,edate)
  
  brkctrl <- "1 month"
  dltdays <- difftime(dpedate,dpsdate,"days") 
  if (dltdays<30) brkctrl <- "1 day"
  
  gp <- ggplot(ddf,aes_string(x=x,y=y)) + 
             geom_point(aes_string(color=series),na.rm=T)  +
             xlab(xlab) + ylab(ylab) + ggtitle(mtit) +
             scale_x_datetime("Date",breaks = date_breaks(brkctrl),limits=c(dpsdate,dpedate)) +
             theme(axis.text.x = element_text(angle = 30, hjust = 1))

  gp <- addVlinesAndText(vlines,gp)

  gp <- addBackground(backg,gp)
  
  hp <- ggplot(ddf) + geom_histogram(aes_string(x=y),bins=30)
  hp <- addBackground(backg,hp)
  
  ghp <- grid.arrange(gp, hp, ncol=2,widths = c(2,1))

  return(ghp)
}
```

## Read in consolidated chat, call, and session volume data

```{r}
stload <- Sys.time()
tfname <- sprintf("%s/%s",fpath,"colsolidatedTorontoData01.csv")
condf <- read.csv(tfname)

minsessfilt <- 5000
nbef <- nrow(condf)
condf <- condf %>% filter(minsessfilt<actsess)
naft <- nrow(condf)
print(sprintf("Filtered %d of %d hours because sessions less than %d",(nbef-naft),naft,minsessfilt))
condf <- condf %>% mutate( dt = as.POSIXct(dt,tz=tztz) ) %>%
                   mutate( log_winchib = log(winchib) ) %>%
                   mutate( log_wincall = log(wincall) ) %>%
                   mutate( log_xbxchib = log(xbxchib) ) %>%
                   mutate( log_xbxcall = log(xbxcall) ) %>%
                   mutate( rate_winchib = winchib/actsess ) %>%
                   mutate( rate_wincall = wincall/actsess ) %>%
                   mutate( rate_xbxchib = xbxchib/actsess ) %>%
                   mutate( rate_xbxcall = xbxcall/actsess ) 

dcondf <- condf %>% group_by(dnum) %>% summarise(dt=min(dt),
                                                 totchib=sum(totchib),winchib=sum(winchib),xbxchib=sum(xbxchib),
                                                 totcall=sum(totcall),wincall=sum(wincall),xbxcall=sum(xbxcall),
                                                 actsess=sum(actsess),actuser=sum(actuser)
                                                 )

elap <- as.numeric((Sys.time()-stload)[1],units="secs")
print(sprintf("Loading consolidated data took %.1f secs",elap))
```


# chats

```{r fig.width=14, fig.height=6, echo=T}
if (verbose>=2){
  pltdf <- dcondf %>% gather(series,chib,-dt) %>% filter(series %in% c("totchib","winchib","xbxchib"))
  dailyplot(pltdf,"dt","chib",series="series",mtit="Chats In Block",ylab="Sum",vlines=totdates,backg=totback)
}
```

```{r fig.width=14, fig.height=6, echo=T}
if (verbose>=2){
  pltdf <- dcondf %>% gather(series,call,-dt) %>% filter(series %in% c("totcall","wincall","xbxcall"))
  dailyplot(pltdf,"dt","call",series="series",mtit="Calls",ylab="Sum",vlines=totdates,backg=totback)
}
```


```{r fig.width=14, fig.height=6, echo=T}
if (verbose>=2){
  pltdf <- dcondf %>% gather(series,active,-dt) %>% filter(series %in% c("actsess","actuser"))
  dailyplot(pltdf,"dt","active",series="series",mtit="Sessions",ylab="Sum",vlines=totdates,backg=totback)
}
```

## regression code
```{r fig.width=14, fig.height=6, echo=T}
results <- list()
initResults <- function(){
  results <<- list()
}
  
addToResults <- function(newresults){
  results[[length(results)+1]] <<- newresults
}
listtodf <- function(lst){
  nr <- length(lst)    # rows
  if (nr==0) return(NULL)
  nvek <- names(lst[[1]])
  nc <- length(nvek)   # columns
  df <- data.frame(idx=1:nr) # preallocate length
  for (i in 1:nc){
    iname <- nvek[i]
    df[[iname]] <- sapply(lst,`[[`,iname)
  }
  df$idx <- NULL # no longer needed
  return(df)
}
getResults <- function(){
  return(listtodf(results))
}

getregdf <- function(df,vname,discdate,befdays,aftdays,dates){
  
  # filter on time
  sregdate <- discdate - days(befdays)
  eregdate <- discdate + days(aftdays)
  df <- df %>% filter( sregdate <= dt & dt <= eregdate) 
  
  df <- df %>% mutate( hour=as.factor(hour(dt)) ) %>%
               mutate( dow=as.factor(wday(dt))) %>%  
               mutate( idx=1:nrow(df) ) 

  # add level variables
  cutidx <- which(df$dt==discdate)

    df <- df %>% mutate( lin1=if_else(idx<cutidx,idx-cutidx,0L)) %>%
                 mutate( lin2=if_else(idx<cutidx,0L,idx-cutidx)) %>%
                 mutate( postchange=if_else(idx<cutidx,0L,1L) )

  return(df)
}
formlist = list(
  model1="%s ~ hour + dow + lin1 + lin2 + postchange"
)
doregression <- function(df,vname,modelselector,chgdate,befdays,aftdays){
  df <- getregdf(df,vname,chgdate,befdays,aftdays,dates)
  formstr <- sprintf(formlist[[modelselector]],vname)
  form <- as.formula(formstr)
  fit <- glm(form,data=df)
  summary_fit <- summary(fit)
  coeftest_fit <- coeftest(fit, vcov = vcovHC(fit, "HC1"))
  if (verbose>0){
    print(summary_fit)
    print(coeftest_fit)
  }
  df$resid <- resid(fit)
  df$predicted <-  df[[vname]]-df$resid
  ffit <<- fit
  sfit <<- summary_fit
  cfit <<- coeftest_fit
  return(list(df=df,formstr=formstr,fit=fit,sfit=summary_fit,cfit=coeftest_fit))
}
regress <- function(df,vname,modelselector,dates,chgdate,mtit1,befdays=7,aftdays=7){
  crk <- crackdate(chgdate)
  idx <- length(results)+1
  
  print(sprintf("%d Regression for %s %s on %s",idx,vname,modelselector,chgdate))


  rv <- doregression(df,vname,modelselector,crk$date,befdays,aftdays)
  if (verbose>0){
    # this is a bit of a hack, must address sometime
    bkgrnd <- smcback
    if (dates[1]==xbxdates[1]){
      bkgrnd <- xbxback
    }
    df1 <- rv$df %>%  gather_("series",vname,c(vname,"predicted"))
    mtit <- sprintf("%d - %s - %s",idx,mtit1,rv$formstr)
    plt <- dailyplot(df1,"dt",vname,series="series",mtit,ylab="Sum",
                     vlines=dates,backg=bkgrnd,ovsdate=min(df1$dt),ovedate=max(df1$dt))
    print(plt)
    mtit <- sprintf("%d - Residuals - %s - %s",idx,mtit1,rv$formstr)
    plt <- residplot(df1,"dt","resid",mtit,ylab="Sum",vlines=dates,backg=bkgrnd,ovsdate=min(df1$dt),ovedate=max(df1$dt))
   # print(plt)
  }
  newresults <- list(var=vname,
                     title=mtit1,
                     chgDate=crk$sdate,
                     chgVal=crk$sval,
                     model=modelselector,
                     formula=rv$formstr,
                     chgCoef.fit=rv$fit$coefficients["postchange"],
                     chgCoef.smry=rv$sfit$coefficients["postchange",1],
                     chgStd.smry=rv$sfit$coefficients["postchange",2],
                     chgTval.smry=rv$sfit$coefficients["postchange",3],
                     chgPval.smry=rv$sfit$coefficients["postchange",4],
                     chgZval.cfit=rv$cfit["postchange","z value"],
                     chgPval.cfit=rv$cfit["postchange","Pr(>|z|)"]
                     )
  addToResults(newresults)
}
regressoverdates <- function(df,vname,modelselector,dates,title,befdays=7,aftdays=7){
  for (chgdate in dates){
    regress(condf,vname,modelselector,dates,chgdate,title,befdays=befdays,aftdays=aftdays) 
  }
}
```




```{r fig.width=14, fig.height=6, echo=T}
initResults()

# SMC - model 1
if (justdoone){
  regressoverdates(condf,"winchib","model1",smcdates,"SMC - Hourly Chats")
} else {
  regressoverdates(condf,"winchib","model1",smcdates,"SMC - Hourly Chats")
  regressoverdates(condf,"log_winchib","model1",smcdates,"SMC - log(Hourly Chats)")
  regressoverdates(condf,"rate_winchib","model1",smcdates,"SMC - Hourly Chat Rate per Session")
  
  regressoverdates(condf,"wincall","model1",smcdates,"SMC - Hourly Chats")
  regressoverdates(condf,"log_wincall","model1",smcdates,"SMC - log(Hourly Chats)")
  regressoverdates(condf,"rate_wincall","model1",smcdates,"SMC - Hourly Chat Rate per Session")
  
  # XBX - model 1
  regressoverdates(condf,"xbxchib","model1",xbxdates,"Xbox - Hourly Chats")
  regressoverdates(condf,"log_xbxchib","model1",xbxdates,"Xbox - log(Hourly Chats)")
  regressoverdates(condf,"rate_xbxchib","model1",xbxdates,"Xbox - Hourly Chat Rate per Session")
  
  regressoverdates(condf,"xbxcall","model1",xbxdates,"Xbox - Hourly Chats")
  regressoverdates(condf,"log_xbxcall","model1",xbxdates,"Xbox - log(Hourly Chats)")
  regressoverdates(condf,"rate_xbxcall","model1",xbxdates,"Xbox - Hourly Chat Rate per Session")
}
```

# Results

```{r echo=F}
starval <- function(val){
  n <- length(val)
  sv <- rep("|   ",n)
  sv[ val<=0.1   ] <- "| . "
  sv[ val<=0.05  ] <- "| *  "
  sv[ val<=0.01  ] <- "| ** "
  sv[ val<=0.001 ] <- "| ***"
  return(sv)
}
options(width=2000)
df <- getResults()
df$idx <- 1:nrow(df)
kdf <- df[,c("idx","title","model","formula","chgDate","chgVal","chgCoef.fit","chgCoef.smry","chgStd.smry","chgZval.cfit","chgPval.cfit")]
kdf <- kdf %>% mutate(s=starval(chgPval.cfit))

kable(kdf,format="html",padding=5)
```


## Done
```{r echo=F}
elap <- as.numeric((Sys.time()-starttime)[1],units="secs")
print(sprintf("%s created on %s took %.1f secs",versionstring,startfmttime,elap))
```