---
title: "Model-DID Regressions - V04"
author: "Mike Wise"
date: "30 April 2017"
output: html_document
---
<STYLE TYPE="text/css">
<!--
  td{
    font-family: Arial; 
    font-size: 10pt;
    padding:0px;
    border:1px solid #d0d0d0;
  }
  th {
    font-family: Arial; 
    font-size: 7pt;
    height: 20px;
    font-weight: bold;
    text-align: center;
    padding:0px;
    background-color: #ccccff;
    border:1px solid #808080;
  }
  table { 
    border-spacing: 18px 0px;
    border-collapse: collapse;
    border:1px solid #000000;
  }
--->
</STYLE>

<style>
.main-container { width: 1280px; max-width:2800px;}
</style>



```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
hook_output <- knitr::knit_hooks$get("output")


knitr::knit_hooks$set(output=function(x,options){
  xn <- hook_output(x,options)
  # interestingly xn is a big character string. 
  # I had expected a list or vector, but the length of x is 1 and the class is character.

  # The following regexp extracts the parameters from a statement of the form
  # htmlesc<<(pat1,pat2)>> and converts it to <pat1>pat2</pat1>
  xn <- gsub("## htmlesc<<([^,]*),{1}([^>>]*)>>","\n```\n<\\1>\\2</\\1>\n```\n",xn)
  # now remove double escaped lines that occur when we do these right after each other
  gsub(">\n```\n\n\n```\n<",">\n<",xn)
}
)
options(width=200)

```

Data pre-processed and analyzied from chat logs and web logs by Marcus Collins. 

Analysis based on R-Scripts from Jacob LaRiviere.

R-Markdown and plots from Mike Wise.

## Initialization of libraries
```{r, message=F}
library(tidyverse,quietly=T,warn.conflicts=F)
library(lubridate,quietly=T,warn.conflicts=F)
library(scales,quietly=T,warn.conflicts=F)
library(zoo,quietly=T,warn.conflicts=F)
library(lmtest,quietly=T,warn.conflicts=F)
library(sandwich,quietly=T,warn.conflicts=F)
library(gridExtra,quietly=T,warn.conflicts = F)
library(knitr,quietly=T,warn.conflicts = F)
```

Set random seeds, record start time and version.

```{r}
set.seed(1234)
version <-0.4
versionstring <- sprintf("Version %.1f",version)

starttime <- Sys.time()
startfmttime <- sprintf(format(starttime, "%d %b %Y - %H:%M:%S"))

print(sprintf("%s created on %s",versionstring,startfmttime))
```


#### Various constants

```{r}
tztz <- "UTC"  # Apparently all of our time zones are UTC...
s2date <- function(strdate){
  return(as.POSIXct(strdate,tz=tztz))
}
firstday <- s2date("2015-01-01")  # we will count days from the first day in 2015

smcdates <- c("2016-08-17 07:00/red/0-30%",
              "2016-09-01 07:00/red/30-50%",
              "2016-09-07 07:00/red/50-100%")
xbxdates <- c("2016-10-11 07:00/purple/0-10%",
              "2016-10-18 07:00/purple/10-30%",
              "2016-11-01 07:00/purple/30-50%",
              "2016-12-15 08:00/purple/50-90%",
              "2016-11-17 08:00/blue/content change")
totdates <- c(smcdates,xbxdates)
smcback <- "lightsteelblue1"
xbxback <- "darkseagreen2"
xabback <- "darkseagreen3"
totback <- "wheat"

fpath <- "TorontoData"
sdate <- s2date("2016-06-01")
mdate <- s2date("2017-01-01")
edate <- s2date("2017-03-07")
verbose <- 2
```

#### Misc utility functions

```{r}
crackdate <- function(datestr){
  sar <- unlist(strsplit(datestr,"/"))
  sdate <- sar[[1]]
  date <- s2date(sdate)
  val <- 0
  sval <- sar[[3]]
  levpart <- sar[[3]]
  pctpresent <- F
  if (grepl("%",levpart)){
    levpart <- gsub("%","",levpart)
    val <- as.numeric(unlist(strsplit(levpart,"-"))[[2]])
    sval <- gsub("-","_",levpart)
    pctpresent <- T
  }
  return(list(date=date,sdate=sdate,val=val,sval=sval,pctpresent=pctpresent))
}

addStepDateToVek <- function(dates,idx,dtvek,vvek){
  cd1 <- crackdate(dates[[idx]])
  if (!cd1$pctpresent){
    # if there is no % don't do anything
    return(vvek)
  }
  dt1 <- cd1$date
  if (idx<length(dates)){
    cd2 <- crackdate(dates[[idx+1]])
    dt2 <- cd2$date
  } else {
    dt2 <- max(dtvek)
  }
  #print("addstepdate")
  #print(dt1)
  #print(dt2)
  val <- cd1$val
  tochg <-  dt1<=dtvek & dtvek<= dt2
  vvek[ tochg ] <- val
  #print(sprintf("changed %d values to %d",sum(tochg),val))
  return(vvek)
}
getStepDates <- function(dates,dtvek){
 vvek <- rep(0,length(dtvek))
 for (i in 1:length(dates)){
   vvek <- addStepDateToVek(dates,i,dtvek,vvek)
 }
 return(vvek)
}
getSmcStepDates <- function(dtvek){
 return(getStepDates(smcdates,dtvek))
}
getXabStepDates <- function(dtvek){
 return(getStepDates(xbxdates,dtvek))
}
```



#### Plot functions


```{r}
addVlinesAndText <- function(vlines,gp){
  if (is.null(vlines)) return(gp) # do nothing in this case
  
  # split the lines and convert to data.frame
  sar <- strsplit(vlines,"/")
  # the following reforms the date strings into a data.frame for geom_vline
  ldf <- data.frame(t(matrix(unlist(sar),length(sar[[1]]),length(sar)))) #tricky
  names(ldf) <- c("dt","clr","lab")
  ldf$dt <- s2date(ldf$dt)
  ldf$ndt <- as.numeric(ldf$dt)
  # add a newline to the front so as to display the text 
  # this keeps the text from writing on top of the vline
  
  ldf$lab <- paste0("\n",ldf$lab) 
  # now actually add the verticle lines and the text 
  gp <- gp + geom_vline(xintercept=ldf$ndt,color=ldf$clr) +
             annotate(geom="text",x=ldf$dt,y=0,label=ldf$lab,color=ldf$clr,hjust=0,angle=90,na.rm=T)
  return(gp)
}
addBackground <- function(backg,gp){
  if (is.null(backg)) return(gp) # do nothing in this case
  gp <- gp + theme(panel.background = element_rect(fill = backg))
  return(gp)
}
overdate <- function(ovdate,defdate){
  # date override
  rv <- defdate
  if (!is.null(ovdate)) { 
    rv <- ovdate
  }
  return(rv)
}
dailyplot <- function(ddf,x,y,mtit="",xlab="date",stit=NULL,
                      ylab=NULL,vlines=NULL,backg=NULL,series=NULL,clrs=NULL,
                      ovsdate=NULL,ovedate=NULL,rotxaxtxt=0){
  # Single series plot  with monthly breaks on the x-axis
  
  # override dates if needed
  dpsdate <- overdate(ovsdate,sdate)
  dpedate <- overdate(ovedate,edate)
  
  brkctrl <- "1 month"
  dltdays <- difftime(dpedate,dpsdate,"days") 
  if (dltdays<30) brkctrl <- "1 day"
  
  gp <- ggplot(ddf,aes_string(x=x,y=y)) + 
             geom_line(aes_string(color=series),na.rm=T)  +
             labs(title=mtit,xlab=xlab,ylab=ylab,subtitle=stit) +
             scale_x_datetime("Date",breaks = date_breaks(brkctrl),limits=c(dpsdate,dpedate))

  gp <- addVlinesAndText(vlines,gp)

  gp <- addBackground(backg,gp)
  
  if (rotxaxtxt!=0){
    gp <- gp + theme(axis.text.x = element_text(angle = rotxaxtxt, hjust = 0))
  }
  if (!is.null(clrs)){
    gp <- gp + scale_color_manual(values=clrs)
  }

  return(gp)
}
residplot <- function(ddf,x,y,mtit="",xlab="date",ylab=NULL,vlines=NULL,backg=NULL,series=NULL,ovsdate=NULL,ovedate=NULL){
  # Single series plot  with monthly breaks on the x-axis
  
  # override dates if needed
  dpsdate <- overdate(ovsdate,sdate)
  dpedate <- overdate(ovedate,edate)
  
  brkctrl <- "1 month"
  dltdays <- difftime(dpedate,dpsdate,"days") 
  if (dltdays<30) brkctrl <- "1 day"
  
  gp <- ggplot(ddf,aes_string(x=x,y=y)) + 
             geom_point(aes_string(color=series),na.rm=T)  +
             xlab(xlab) + ylab(ylab) + ggtitle(mtit) +
             scale_x_datetime("Date",breaks = date_breaks(brkctrl),limits=c(dpsdate,dpedate)) +
             theme(axis.text.x = element_text(angle = 30, hjust = 1))

  gp <- addVlinesAndText(vlines,gp)

  gp <- addBackground(backg,gp)
  
  hp <- ggplot(ddf) + geom_histogram(aes_string(x=y),bins=30)
  hp <- addBackground(backg,hp)
  
  ghp <- grid.arrange(gp, hp, ncol=2,widths = c(2,1))

  return(ghp)
}
```

## Read in consolidated chat, call, and session volume data

```{r}
stload <- Sys.time()
tfname <- sprintf("%s/%s",fpath,"colsolidatedTorontoData02.csv")
condf <- read.csv(tfname)

minsessfilt <- 5000
nbef <- nrow(condf)
condf <- condf %>% filter(minsessfilt<actsess)
naft <- nrow(condf)
print(sprintf("Filtered %d of %d hours because sessions less than %d",(nbef-naft),naft,minsessfilt))

condf <- condf %>% mutate( dt = as.POSIXct(dt,tz=tztz) ) %>%
                   mutate( log_winchib = log(winchib) ) %>%
                   mutate( log_wincall = log(wincall) ) %>%
  
                   mutate( log_xbxchib = log(xbxchib) ) %>%
                   mutate( log_xtkchib = log(xtkchib) ) %>%
                   mutate( log_xabchib = log(xabchib) ) %>%
  
                   mutate( log_xbxcall = log(xbxcall) ) %>%
                   mutate( log_xtkcall = log(xtkcall) ) %>%
                   mutate( log_xabcall = log(xabcall) ) %>%
                     
                   mutate( rate_winchib = winchib/actsess ) %>%
                   mutate( rate_wincall = wincall/actsess ) %>%
                     
                   mutate( rate_xbxchib = xbxchib/actsess ) %>%
                   mutate( rate_xtkchib = xtkchib/actsess ) %>%
                   mutate( rate_xabchib = xabchib/actsess ) %>%
                     
                   mutate( rate_xbxcall = xbxcall/actsess ) %>%
                   mutate( rate_xtkcall = xtkcall/actsess ) %>%
                   mutate( rate_xabcall = xabcall/actsess ) 


dcondf <- condf %>% group_by(dnum) %>% summarise(dt=min(dt),
                                                 totchib=sum(totchib),winchib=sum(winchib),xbxchib=sum(xbxchib),
                                                 totcall=sum(totcall),wincall=sum(wincall),xbxcall=sum(xbxcall),
                                                 actsess=sum(actsess),actuser=sum(actuser)
                                                 )

elap <- as.numeric((Sys.time()-stload)[1],units="secs")
print(sprintf("Loading consolidated data took %.1f secs",elap))
```


# chats

```{r fig.width=14, fig.height=6, echo=T}
if (verbose>=2){
  pltdf <- dcondf %>% gather(series,chib,-dt) %>% filter(series %in% c("totchib","winchib","xbxchib"))
  dailyplot(pltdf,"dt","chib",series="series",mtit="Chats In Block",ylab="Sum",vlines=totdates,backg=totback)
}
```
# calls

```{r fig.width=14, fig.height=6, echo=T}
if (verbose>=2){
  pltdf <- dcondf %>% gather(series,call,-dt) %>% filter(series %in% c("totcall","wincall","xbxcall"))
  dailyplot(pltdf,"dt","call",series="series",mtit="Calls",ylab="Sum",vlines=totdates,backg=totback)
}
```
# sessions

```{r fig.width=14, fig.height=6, echo=T}
if (verbose>=2){
  pltdf <- dcondf %>% gather(series,active,-dt) %>% filter(series %in% c("actsess","actuser"))
  dailyplot(pltdf,"dt","active",series="series",mtit="Sessions",ylab="Sum",vlines=totdates,backg=totback)
}
```

## regression code

```{r fig.width=14, fig.height=6, echo=T}
results1 <- list()
results2 <- list()
initResults <- function(){
  results1 <<- list()
  results2 <<- list()
}
  
addToResults1 <- function(newresults){
  results1[[length(results1)+1]] <<- newresults
}
addToResults2 <- function(newresults){
  results2[[length(results2)+1]] <<- newresults
}
listtodf <- function(lst){
  nr <- length(lst)    # rows
  if (nr==0) return(NULL)
  nvek <- names(lst[[1]])
  nc <- length(nvek)   # columns
  df <- data.frame(idx=1:nr) # preallocate length
  for (i in 1:nc){
    iname <- nvek[i]
    df[[iname]] <- sapply(lst,`[[`,iname)
  }
  return(df)
}
getResults1 <- function(){
  return(listtodf(results1))
}
getResults2 <- function(){
  return(listtodf(results2))
}

formlist = list(
  formel1="%s ~ hour + dow + lin1 + lin2 + postchange",
  formel2a="%s ~ hour * dow - 1",
  formel2b="%s ~ lin1 + lin2 + postchange",
  formel2c="%s ~ Dc + Dt + DD",
  formeldid="%s ~ Dc + Dt + DD + as.factor(HOD) + as.factor(DOW)"
#  formel2b="%s ~ lin0 + postchange"
)

```


```{r}
doregressiondid <- function(df,vname,formel,verbosetxt=1){


  formstr <- sprintf(formlist[[formel]],vname)
  form <- as.formula(formstr)
  fit <- glm(form,data=df)
  summary_fit <- summary(fit)
  coeftest_fit <- coeftest(fit, vcov = vcovHC(fit, "HC1"))
  if (verbosetxt>1){
    print(summary_fit)
  }
  if (verbosetxt>0){
    print(coeftest_fit)
  }
  df$resid <- resid(fit)
#  df$predicted <-  df[[vname]]-df$resid
  df$predicted <-  predict(fit,df)
  # for debugging
  ffit <<- fit
  sfit <<- summary_fit
  cfit <<- coeftest_fit

  return(list(df=df,formstr=formstr,fit=fit,sfit=summary_fit,cfit=coeftest_fit))
}

getregdfdid <- function(odf,vname,vname_ctr,vname_trt,sdate,befdays=7,aftdays=7){
  odf$DOW <- wday(odf$dt)
  odf$HOD <- hour(odf$dt)
  df <- odf[c("dt","HOD","DOW",vname_ctr,vname_trt)]

  df <- df %>% gather(series,vname,c(-dt,-HOD,-DOW))
  df[vname] <- df$vname
  df$vname <- NULL
  

  print(sdate)
  crk <- crackdate(sdate)

  sregdate <- crk$date - days(befdays)
  eregdate <- crk$date + days(aftdays)
  print(sprintf("getregdfdid - sdate:%s sregdate:%s eregdate:%s",
                             sdate,sregdate,eregdate))
  
  df <- df %>% filter( sregdate<=dt & dt<= eregdate )
  
  cutdate <- crk$date 
  scutidx <- which(df$dt==cutdate)
  print(crk$sdate)
  print(scutidx)
  print(sprintf("scutidx:%d",scutidx))
  
  df <- df  %>% mutate( Dc = ifelse(series==vname_trt,1L,0L) ) %>%
                mutate( idx = 1:nrow(df) ) %>%
                mutate( Dt = ifelse(dt>crk$date,1L,0L) ) %>%
                mutate( DD = Dt*Dc )
  
  # Print out a summary of the numeric columns for debugging
    regdf <- df
    regdf$series <- NULL
    print(summary(regdf))
  
  return(df)
}

getclrs <- function(vname,vname_ctr,vname_trt){
  cn1 <- paste( vname_ctr,vname,sep="-")
  cn2 <- paste0(vname_ctr,"-predicted")
  cn3 <- paste( vname_trt,vname,sep="-")
  cn4 <- paste0(vname_trt,"-predicted")
  clrs <- c("darkcyan","purple","red","darkgreen")
  names(clrs) <- c(cn1,cn2,cn3,cn4)
  clrs
}

regressdid <- function(df,vname,vname_ctr,vname_trt,dates,chgdate,
                        area,backg,mtit1,befdays=7,aftdays=7,model="model-did"){

  idx <- length(results1)+1
  
  rdf <- getregdfdid(df,vname,vname_ctr,vname_trt,chgdate,befdays,aftdays)
  rv <- doregressiondid(rdf,vname,"formeldid")
  rrv <<- rv
  if (verbose>0){
  #  df1 <- rv$df %>%  gather_("series",vname,c(vname,"predicted"))
    
    # build plot dataframe
    pdf <- rv$df[c("dt","series",vname,"predicted")]
    pdf <- gather(pdf,nseries,value,-dt,-series)
    pdf$series <- paste(pdf$series,pdf$nseries,sep="-")
    pdf[vname] <- pdf$value

    mtit <- sprintf("%d - %s : %s",idx,mtit1,rv$formstr)
    stit <- sprintf("Control: %s Treatment:%s",vname_ctr,vname_trt)
    clrs <- getclrs(vname,vname_ctr,vname_trt)
    plt <- dailyplot(pdf,"dt",vname,series="series",mtit,stit=stit,ylab="Sum",clrs=clrs,
                     vlines=chgdate,backg=backg,ovsdate=min(rv$df$dt),ovedate=max(rv$df$dt),rotxaxtxt=-30)
    print(table(pdf$series))
    suppressWarnings(print(plt))
    mtit <- sprintf("%d - DID Residuals - %s",idx,mtit1)
    plt <- residplot(rv$df,"dt","resid",mtit,ylab="Sum",
                     vlines=chgdate,backg=backg,ovsdate=min(rv$df$dt),ovedate=max(rv$df$dt))
  }
  crk <- crackdate(chgdate)
  newresults <- list(var=vname,
                     title=mtit1,
                     chgDate=crk$sdate,
                     chgVal=crk$sval,
                     model=model,
                     formula=rv$formstr,
                     chgCoef.fit=rv$fit$coefficients["DD"],
                     chgCoef.smry=rv$sfit$coefficients["DD",1],
                     chgStd.smry=rv$sfit$coefficients["DD",2],
                     chgTval.smry=rv$sfit$coefficients["DD",3],
                     chgPval.smry=rv$sfit$coefficients["DD",4],
                     chgZval.cfit=rv$cfit["DD","z value"],
                     chgPval.cfit=rv$cfit["DD","Pr(>|z|)"]                     
                     )
  addToResults1(newresults)
}

regressoverdatesdid <- function(model,df,vname,vname_ctr,vname_trt,area,title,befdays=7,aftdays=7){
  dates <- xbxdates
  backg <- xbxback
  atit <- sprintf("%s - %s",area,title)
  for (chgdate in dates){
    switch(model,
    "model-did"=regressdid(condf,vname,vname_ctr,vname_trt,dates,chgdate,
                                  area,backg,atit,befdays=befdays,aftdays=aftdays)
    )
  }
}
```


```{r fig.width=14, fig.height=6, echo=T}
initResults()

justdoone <- F

# we just want DID with Xbox
m <- "model-did"
if (justdoone){
  regressoverdatesdid(m,condf,"chats","xtkchib","xabchib","Xbox","Hourly Chats")
} else {
  regressoverdatesdid(m,condf,     "chats",     "xtkchib",     "xabchib","Xbox","Hourly Chats")
  regressoverdatesdid(m,condf, "log_chats", "log_xtkchib", "log_xabchib","Xbox","log(Hourly Chats)")
  regressoverdatesdid(m,condf,"rate_chats","rate_xtkchib","rate_xabchib","Xbox","Hourly Chat Rate")
  
  regressoverdatesdid(m,condf,     "calls",     "xtkcall",     "xabcall","Xbox","Hourly Calls")
  regressoverdatesdid(m,condf, "log_calls", "log_xtkcall", "log_xabcall","Xbox","log(Hourly Calls)")
  regressoverdatesdid(m,condf,"rate_calls","rate_xtkcall","rate_xabcall","Xbox","Hourly Call Rate")
}
```

# Model DID Results


```{r echo=F}
starval <- function(val){
  n <- length(val)
  sv <- rep(" |   ",n)
  sv[ val<=0.1   ] <- " | .  "
  sv[ val<=0.05  ] <- " | *  "
  sv[ val<=0.01  ] <- " | ** "
  sv[ val<=0.001 ] <- " | ***"
  return(sv)
}

df <- getResults1()
kdf <- df[,c("idx","title","formula","chgDate","chgVal","chgCoef.fit","chgCoef.smry","chgStd.smry","chgZval.cfit","chgPval.cfit")]
kdf$formula <- sprintf(".   %s",kdf$formula)
kdf$chgDate <- sprintf(".   %s  .",kdf$chgDate)
kdf$chgVal  <- sprintf(".   %s",kdf$chgVal)
kdf <- kdf %>% mutate(sig=starval(chgPval.cfit))
kable(kdf,format="html",padding=0,digits=4)
```



## Done
```{r echo=F}
elap <- as.numeric((Sys.time()-starttime)[1],units="secs")
print(sprintf("%s created on %s took %.1f secs",versionstring,startfmttime,elap))
```