---
title: "Simplify Read"
author: "Mike Wise"
date: "16 Mar 2017"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Data pre-processed and analyzied from call volume logs and web logs by Marcus Collins. 

Analysis based on R-Scripts from Jacob LaRiviere.

R-Markdown and plots from Mike Wise.

## Library Initialization
```{r, message=F}
library(tidyverse,quietly=T,warn.conflicts=F)
library(lubridate,quietly=T,warn.conflicts=F)
library(scales,quietly=T,warn.conflicts=F)
```

#### Set random seeds, record start time and version.

```{r}
set.seed(1234)
version <-0.1
versionstring <- sprintf("Version %.1f",version)

starttime <- Sys.time()
startfmttime <- sprintf(format(starttime, "%d %b %Y - %H:%M:%S"))

print(sprintf("%s created on %s",versionstring,startfmttime))
```

#### Various constants

```{r}
tztz <- "UTC"  # Apparently all of our time zones are UTC...
firstday <- as.POSIXct("2015-01-01",tz=tztz)  # we will count days from the first day in 2015

smcdates <- c("2016-08-17/red/0-30%","2016-09-1/red/30-50%","2016-09-07/red/50-100%")
xtotdates <- c("2016-10-11/purple/0-10%","2016-10-18/purple/10-30%","2016-11-01/purple/30-50%","2016-12-15/purple/50-90%",
              "2016-11-17/blue/content change")
totdates <- c(smcdates,xtotdates)
smcback <- "lightsteelblue1"
xbxback <- "darkseagreen2"
xabback <- "darkseagreen3"
totback <- "wheat"

fpath <- "../TorontoData"
sdate <- as.POSIXct("2016-06-01",tz=tztz)
mdate <- as.POSIXct("2017-01-01",tz=tztz)
edate <- as.POSIXct("2017-02-01",tz=tztz)
```

#### Misc utility functions

```{r}
addStepDateToVek <- function(dates,idx,dtvek,vvek){
  sar1 <- unlist(strsplit(dates[[idx]],"/"))
  datepart1 <- sar1[[1]]
  levpart1 <- sar1[[3]]
  if (!grepl("%",levpart1)){
    # if there is no % don't do anything
    return(vvek)
  }
  dt1 <- as.POSIXct(datepart1,tz=tztz)
  if (idx<length(dates)){
    sar2 <- unlist(strsplit(dates[[idx+1]],"/"))
    datepart2 <- sar2[[1]]
    dt2 <- as.POSIXct(datepart2,tz=tztz)
  } else {
    dt2 <- max(dtvek)
  }
  #print(dt1)
  #print(dt2)
  val <- as.numeric(gsub("%","",unlist(strsplit(levpart1,"-"))[[2]]))
  tochg <-  dt1<=dtvek & dtvek<= dt2
  vvek[ tochg ] <- val
  #print(sprintf("changed %d values to %d",sum(tochg),val))
  return(vvek)
}
getStepDates <- function(dates,dtvek){
 vvek <- rep(0,length(dtvek))
 for (i in 1:length(smcdates)){
   vvek <- addStepDateToVek(dates,i,dtvek,vvek)
 }
 return(vvek)
}
getSmcStepDates <- function(dtvek){
 return(getStepDates(smcdates,dtvek))
}
getXabStepDates <- function(dtvek){
 return(getStepDates(xtotdates,dtvek))
}


```


#### Plot Functions

Plots created using ggplot2


```{r}
addVlinesAndText <- function(vlines,gp){
  if (is.null(vlines)) return(gp) # do nothing in this case
  
  # split the lines and convert to data.frame
  sar <- strsplit(vlines,"/")
  # the following reforms the date strings into a data.frame for geom_vline
  ldf <- data.frame(t(matrix(unlist(sar),length(sar[[1]]),length(sar)))) #tricky
  names(ldf) <- c("dt","clr","lab")
  ldf$dt <- as.POSIXct(ldf$dt,tz=tztz)
  ldf$ndt <- as.numeric(ldf$dt)
  # add a newline to the front so as to display the text 
  # this keeps the text from writing on top of the vline
  
  ldf$lab <- paste0("\n",ldf$lab) 
  # now actually add the verticle lines and the text 
  gp <- gp + geom_vline(xintercept=ldf$ndt,color=ldf$clr) +
             annotate(geom="text",x=ldf$dt,y=0,label=ldf$lab,color=ldf$clr,hjust=0,angle=90)
  return(gp)
}
addBackground <- function(backg,gp){
  if (is.null(backg)) return(gp) # do nothing in this case
  gp <- gp + theme(panel.background = element_rect(fill = backg))
  return(gp)
}
dailyplot <- function(ddf,x,y,mtit="",xlab="date",ylab=NULL,vlines=NULL,backg=NULL,series=NULL){
  # Single series plot  with monthly breaks on the x-axis
  
  gp <- ggplot(ddf,aes_string(x=x,y=y)) + 
             geom_line(aes_string(color=series),na.rm=T)  +
             xlab(xlab) + ylab(ylab) + ggtitle(mtit) +
             scale_x_datetime("Date",breaks = date_breaks("1 months"),limits=c(sdate,edate))

  gp <- addVlinesAndText(vlines,gp)

  gp <- addBackground(backg,gp)

  return(gp)
}
```




## Read in chat volume data (old)


```{r}
stload <- Sys.time()
readChatVolume <- function(frdate,todate,fname){
  fstload <- Sys.time()

  cfname <- sprintf("%s/%s",fpath,fname)
  lcdf <- read.csv(cfname)  
  temp_date<- as.POSIXct(lcdf$Date,format="%m/%d/%Y %I:%M:%S %p",tz=tztz)
  temp_datehour<- as.POSIXct(lcdf$DateHour,format="%m/%d/%Y %I:%M:%S %p",tz=tztz)

  lcdf  <- lcdf %>% mutate( dt = temp_datehour) %>%
                    mutate( dnum = round(as.numeric(difftime(temp_date,firstday,"days")))) %>%
                    mutate( hnum = dnum*24 + hour(dt))
    
  # restrict rows as different files sometimes have extra colums
  lcdf <- lcdf %>% arrange( dt ) # sort
  lcdf <- lcdf[,c("dt","dnum","hnum","IsSXC","IsSMC","virtualAgent","Subject",
                  "CountryCode","MeanChatDuration","CumulativeChatDuration","ChatsInBlock")]
  n1 <- nrow(lcdf)
  lcdf <- lcdf %>% filter( frdate<=dt & dt<todate)
  n2 <- nrow(lcdf)
  elap <- as.numeric((Sys.time()-fstload)[1],units="secs")
  print(sprintf("Read %d of %d lines from %s in %.1f secs",n2,n1,cfname,elap))
  return(lcdf)
}
cvdf1o <- readChatVolume(sdate,mdate,"chat_volume_duration_features-Aug2016-current.csv")
cvdf2o <- readChatVolume(mdate,edate,"chat_volume_duration_features-2017.csv")

cvdfo <- rbind(cvdf1o,cvdf2o)

cvdfo <- cvdfo %>% filter( CountryCode=="USA" ) %>% arrange( dt )

print(sprintf("Rows after filtering to USA only: %d",nrow(cvdfo)))
elap <- as.numeric((Sys.time()-stload)[1],units="secs")
print(sprintf("Loading data took %.1f secs",elap))

```



## Read in chat volume data (new)

```{r}
stload <- Sys.time()
readChatVolumeNew <- function(frdate,todate,fname){
  fstload <- Sys.time()
  cfname <- sprintf("%s/%s",fpath,fname)
  lcdf <- read.csv(cfname)  
  
  
  lcdf$dt<- as.POSIXct(lcdf$DateHour,format="%m/%d/%Y %I:%M:%S %p",tz=tztz)
  
  #filter early
  n1 <- nrow(lcdf)
  lcdf <- lcdf %>% filter( frdate<=dt & dt<todate)
  n2 <- nrow(lcdf)
  dtd<- as.POSIXct(lcdf$DateHour,format="%m/%d/%Y",tz=tztz)

 # lcdf$temp_date<- as.POSIXct(lcdf$Date,format="%m/%d/%Y %I:%M:%S %p",tz=tztz)
  lcdf  <- lcdf %>% mutate( dnum = round(as.numeric(difftime(dtd,firstday,"days")))) %>%
                    mutate( hnum = dnum*24 + hour(dt))
    
  # restrict rows as different files sometimes have extra colums
  lcdf <- lcdf %>% arrange( dt ) # sort
  lcdf <- lcdf[,c("dt","dnum","hnum","IsSXC","IsSMC","virtualAgent","Subject",
                  "CountryCode","MeanChatDuration","CumulativeChatDuration","ChatsInBlock")]
  elap <- as.numeric((Sys.time()-fstload)[1],units="secs")
  print(sprintf("Read %d of %d lines from %s in %.1f secs",n2,n1,cfname,elap))
  return(lcdf)
}
cvdf1n <- readChatVolumeNew(sdate,mdate,"chat_volume_duration_features-Aug2016-current.csv")
cvdf2n <- readChatVolumeNew(mdate,edate,"chat_volume_duration_features-2017.csv")

cvdfn <- rbind(cvdf1n,cvdf2n)

cvdfn <- cvdfn %>% filter( CountryCode=="USA" ) %>% arrange( dt )

print(sprintf("Rows after filtering to USA only: %d",nrow(cvdfn)))
elap <- as.numeric((Sys.time()-stload)[1],units="secs")
print(sprintf("Loading data took %.1f secs",elap))
```


```{r fig.width=14, fig.height=6, echo=T}
dnew <- cvdfn %>% group_by(dnum) %>% summarise(count=n(),cib=sum(ChatsInBlock))
dold <- cvdfo %>% group_by(dnum) %>% summarise(count=n(),cib=sum(ChatsInBlock))
ddf <- full_join(dnew,dold,by="dnum",suffix=c(".new",".old"))
ddf <- ddf %>% mutate(count.diff=count.new-count.old,cib.diff=cib.new-cib.old)
gdf <- ddf %>% gather(series,count,-dnum,-count.diff,-cib.diff)
ggplot(gdf) + geom_line(aes(dnum,count,color=series))
```
```{r fig.width=14, fig.height=6, echo=T}
hnew <- cvdfn %>% filter(dnum==604) %>% group_by(hnum) %>% summarise(count=n())
hold <- cvdfo %>% filter(dnum==604) %>% group_by(hnum) %>% summarise(count=n())
hdf <- full_join(hnew,hold,by="hnum",suffix=c(".new",".old"))
hdf <- hdf %>% mutate(diff=count.new-count.old)
ghdf <- hdf %>% gather(series,count,-hnum,-diff)
ggplot(ghdf) + geom_line(aes(hnum,count,color=series))
```

## Done

```{r echo=F}
elap <- as.numeric((Sys.time()-starttime)[1],units="secs")
print(sprintf("%s created on %s took %.1f secs",versionstring,startfmttime,elap))
```