---
title: "SMSChat_V5_2"
author: "Toronto"
date: "20 Feb 2017"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Initialzation


```{r}
### XBox Chat data
### Data comes from Marcus Collins' scope script from .ss structured stream called ChatSessionUnified in Cosmos

# These library permit use of heteroskedastic robust standard errors 
library(lmtest)
library(sandwich)
# These are useful for working with strings below
library(tidyverse)
library(stringr)
#library(chron)
library(dplyr)
library(lubridate)
library(insol)


set.seed(1234)

version <-5.2
versionstring <- sprintf("Version %.1f",version)

starttime <- Sys.time()
startfmttime <- sprintf(format(starttime, "%d %b %Y - %H:%M:%S"))
tztz <- "US/Pacific"

print(sprintf("%s created on %s",versionstring,startfmttime))

#setwd("C:/Users/jlariv/Documents/OneDrive for Business/Toronto/Data")
#setwd("C:/Users/jlariv/OneDrive - Microsoft/Toronto/Data")
#fname <- "d:/local/TorontoEffect/data/chat-vol-duration-features.csv"
fname <- "data/chat-vol-duration-features.csv"
```

```{r}
print(getwd())
mydata <- read.csv(fname)
mydata$pbbt <- as.POSIXct(mydata$BlockBeginTime,format="%m/%d/%Y %I:%M:%S %p",tz=tztz)
datestr <- sapply(strsplit(as.character(mydata$Date)," "),'[',1) # strip out the "12:00:00 AM"
mydata$datestr <- paste(datestr,mydata$Hour,sep=" ") # append the hour
mydata$dt <- as.POSIXct(mydata$datestr,format="%m/%d/%Y %H",tz=tztz)
mydata$dtd <- as.POSIXct(mydata$datestr,format="%m/%d/%Y",tz=tztz)

# calculate a daynumber that goes 0-24 hours and handles leap years, DST, etc. correctly
# we will aggregate on this
mydata$dnum <- round(as.numeric(difftime(mydata$dtd,as.POSIXct("2015-01-01",tz=tztz),"days")),0)
```

```{r}

colnames(mydata)
#Keep only XBox USA Chat data
unique(mydata$Subject)
newdata<-mydata

newdata <-newdata[ order(newdata$dt), ]
newdata <- subset(newdata,newdata$dt >= as.POSIXct("2016-07-15",tz=tztz))
newdata <- subset(newdata,newdata$dt < as.POSIXct("2017-01-08",tz=tztz))

# with  group
newdata_USA <- subset(newdata,CountryCode == "USA")
newdata_USA %>%   group_by(Subject) %>%   summarise_each (funs(mean, min, max, sd) , mean_Chats_per_hour = ChatsInBlock)


#ag <- aggregate(. ~ Subject, mydata, function(x) c(mean = mean(ChatsInBlock), sd = sd(ChatsInBlock)))
Xdata <- subset(mydata,Subject == "A&B - Xbox")
```


# Combine and Format 


```{r}
# furthur restrict data
newdata <- subset(newdata,newdata$dt >= as.POSIXct("2016-07-27",tz=tztz))
newdata <- subset(newdata,newdata$dt < as.POSIXct("2017-01-08",tz=tztz))
```



# Daily Plot
```{r}

daily <- group_by(newdata,dnum) %>% summarize(dt=min(dt),ChatsInBlock = sum(ChatsInBlock) )
maxcibs <- max(daily$ChatsInBlock) + 1000
plot(daily$dt, daily$ChatsInBlock,  ylim = c(0,maxcibs),
     main = "Xbox A&B Chat: Raw Data Aggregated to Daily Level", xlab = "Date", ylab = "Chat Initiations", pch=19)
abline(v=as.POSIXct("2016-10-11"),col = "red")
abline(v=as.POSIXct("2016-10-18"),col = "red")
abline(v=as.POSIXct("2016-11-01"),col = "red")
abline(v=as.POSIXct("2016-11-17"),col = "blue")
abline(v=as.POSIXct("2016-12-15"),col = "red")

#POST OCT 1

#Take relevant subset
daily <- subset(daily,daily$dt >= as.POSIXct("2016-10-01",tz=tztz))


#Plot of the raw daily data 
plot(daily$dt, daily$ChatsInBlock,  ylim = c(0,maxcibs),
     main = "Xbox A&B Chat: Raw Data Aggregated to Daily Level", xlab = "Date", ylab = "Chat Initiations", pch=19)
abline(v=as.POSIXct("2016-10-11"),col = "red")
abline(v=as.POSIXct("2016-10-18"),col = "red")
abline(v=as.POSIXct("2016-11-01"),col = "red")
abline(v=as.POSIXct("2016-11-17"),col = "blue")
abline(v=as.POSIXct("2016-12-15"),col = "red")

```



# Create count variable for subsequent merge

```{r}
daily$count <- seq(length(daily$ChatsInBlock))
daily$count2 <- daily$count^2
daily$count3 <- daily$count^3
daily$count4 <- daily$count^4
daily$count5 <- daily$count^5
daily$count6 <- daily$count^6
daily$count7 <- daily$count^7
daily$count8 <- daily$count^8
daily$count9 <- daily$count^9
daily$count10 <- daily$count^10
daily$dtdaily <- daily$dt
colnames(daily)
```

# Merge daily and SUBSET of hourly data


```{r}
vars <- c("dtdaily","count", "count2","count3", "count4","count5", "count6","count7","count8","count9", "count10")
temp <- daily[vars]

newdata1 <- subset(newdata,newdata$dt >= as.POSIXct("2016-10-01",tz=tztz))
# temp$dt is formatted by as.Date from line 45: daily$date_formatted <- as.Date(daily$daily_time) and line 99: daily$dt <- daily$date_formatted
# Must do the same for the newdata1 dataframe
m1 <- merge(temp,newdata1, by.x="dtdaily", by.y = "dtd")
m1 <- m1[order(m1$dt), ]


##########################
#Create dummies with correct initiation date for various treatments.
m1$sky0_10 <- ifelse(m1$dt >= as.POSIXct("2016-10-11",tz=tztz),1,0)
m1$sky10_30 <- ifelse(m1$dt >= as.POSIXct("2016-10-18",tz=tztz),1,0)
m1$sky30_50 <- ifelse(m1$dt >= as.POSIXct("2016-11-01",tz=tztz),1,0)
m1$content <- ifelse(m1$dt >= as.POSIXct("2016-11-17",tz=tztz),1,0)
m1$sky50_90 <- ifelse(m1$dt >= as.POSIXct("2016-12-15",tz=tztz),1,0)

###########################


#Plot of the raw data
plot(m1$dt, m1$ChatsInBlock,  main = "Raw Data Aggregated to Hour Level", xlab = "Date", ylab = "Chat Initiations", pch=19)
abline(v=as.POSIXct("2016-10-11"),col = "red")
abline(v=as.POSIXct("2016-10-18"),col = "red")
abline(v=as.POSIXct("2016-11-01"),col = "red")
abline(v=as.POSIXct("2016-11-17"),col = "blue")
abline(v=as.POSIXct("2016-12-15"),col = "red")

```



# stargazer will help with tables and display of data

```{r}
#library(stargazer)
#Table of summary statistics
#stargazer(m1[c("ChatsInBlock")], type = "text", title="Descriptive statistics", digits=1, out="Summary.txt")
#utils::View(m1)

m1$ln_ChatsInBlock<-log(m1$ChatsInBlock)

#Main specification of 8th order Polynomial levels
reg_poly5_full = glm(ChatsInBlock ~ as.factor(Hour) + as.factor(ChatDOW) + count + count2 + count3 + count4 + count5 + count6 + count7 +count8 + sky0_10 + sky10_30 + sky30_50 + sky50_90 +content, data=m1)
#summary(reg_poly5_full)
#coeftest(reg_poly5_full, vcov = vcovHC(reg_poly5_full, "HC1"))

#Main specification of 8th order Polynomial logs
reg_poly5_full = glm(ln_ChatsInBlock ~ as.factor(Hour) + as.factor(ChatDOW) + count + count2 + count3 + count4 + count5 + count6 + count7 +count8 + sky0_10 + sky10_30 + sky30_50 + sky50_90 +content, data=m1)
#summary(reg_poly5_full)
#coeftest(reg_poly5_full, vcov = vcovHC(reg_poly5_full, "HC1"))


#Main specification of 8th order Polynomial hour by day levels, HOD*DOW
reg_poly5_full = glm(ChatsInBlock ~ as.factor(Hour)*as.factor(ChatDOW) + count + count2 + count3 + count4 + count5 + count6 + count7 +count8 + sky0_10 + sky10_30 + sky30_50 + sky50_90 +content, data=m1)
#summary(reg_poly5_full)
#coeftest(reg_poly5_full, vcov = vcovHC(reg_poly5_full, "HC1"))

#Main specification of 8th order Polynomial hour by day logs, HOD*DOW
reg_poly5_full = glm(ln_ChatsInBlock ~ as.factor(Hour)*as.factor(ChatDOW) + count + count2 + count3 + count4 + count5 + count6 + count7 +count8 + sky0_10 + sky10_30 + sky30_50 + sky50_90 +content, data=m1)
#summary(reg_poly5_full)
#coeftest(reg_poly5_full, vcov = vcovHC(reg_poly5_full, "HC1"))


##### 8TH ORDER RESIDUAL PLOT
reg_hourly_resid_poly8 = glm(ChatsInBlock ~ as.factor(Hour) + as.factor(ChatDOW) + count + count2 + count3 + count4 + count5 + count6 + count7 + count8, data=m1)
m1$hourly_resid_poly8 <- resid(reg_hourly_resid_poly8)
plot(m1$dt, m1$hourly_resid_poly8,  main = "Chat Initiations", xlab = "Date", ylab = "residual (inc 8th Order polynomial, no dummies)")
abline(v=as.POSIXct("2016-10-11"),col = "red")
abline(v=as.POSIXct("2016-10-18"),col = "red")
abline(v=as.POSIXct("2016-11-01"),col = "red")
abline(v=as.POSIXct("2016-11-17"),col = "blue")
abline(v=as.POSIXct("2016-12-15"),col = "red")

##### 8TH ORDER RESIDUAL PLOT
reg_hourly_resid_poly8 = glm(ChatsInBlock ~ as.factor(Hour)*as.factor(ChatDOW) + count + count2 + count3 + count4 + count5 + count6 + count7 + count8, data=m1)
m1$hourly_resid_poly8 <- resid(reg_hourly_resid_poly8)
plot(m1$dt, m1$hourly_resid_poly8,  main = "Chat Initiations", xlab = "Date", ylab = "residual (inc 8th Order polynomial, HOD*DOW, no dummies)")
abline(v=as.POSIXct("2016-10-11"),col = "red")
abline(v=as.POSIXct("2016-10-18"),col = "red")
abline(v=as.POSIXct("2016-11-01"),col = "red")
abline(v=as.POSIXct("2016-11-17"),col = "blue")
abline(v=as.POSIXct("2016-12-15"),col = "red")
```



# No Christmas

```{r}
m2<-subset(m1,m1$dt < as.POSIXct("2016-12-24",tz=tztz))
##### 8TH ORDER RESIDUAL PLOT Levels
reg_hourly_resid_poly8 = glm(ChatsInBlock ~ as.factor(Hour) + as.factor(ChatDOW) + count + count2 + count3 + count4 + count5 + count6 + count7 + count8, data=m2)
m2$hourly_resid_poly8 <- resid(reg_hourly_resid_poly8)
plot(m2$dt, m2$hourly_resid_poly8,  main = "Chat Initiations", xlab = "Date", ylab = "residual (inc 8th Order polynomial, no dummies)")
abline(v=as.POSIXct("2016-10-11"),col = "red")
abline(v=as.POSIXct("2016-10-18"),col = "red")
abline(v=as.POSIXct("2016-11-01"),col = "red")
abline(v=as.POSIXct("2016-11-17"),col = "blue")
abline(v=as.POSIXct("2016-12-15"),col = "red")

##### 8TH ORDER RESIDUAL PLOT Levels, HOD*DOW
reg_hourly_resid_poly8 = glm(ChatsInBlock ~ as.factor(Hour)*as.factor(ChatDOW) + count + count2 + count3 + count4 + count5 + count6 + count7 + count8, data=m2)
m2$hourly_resid_poly8 <- resid(reg_hourly_resid_poly8)
plot(m2$dt, m2$hourly_resid_poly8,  main = "Chat Initiations", xlab = "Date", ylab = "residual (inc 8th Order polynomial, no dummies)")
abline(v=as.POSIXct("2016-10-11"),col = "red")
abline(v=as.POSIXct("2016-10-18"),col = "red")
abline(v=as.POSIXct("2016-11-01"),col = "red")
abline(v=as.POSIXct("2016-11-17"),col = "blue")
abline(v=as.POSIXct("2016-12-15"),col = "red")


#Main specification of 8th order Polynomial levels
reg_poly5_full = glm(ChatsInBlock ~ as.factor(Hour) + as.factor(ChatDOW) + count + count2 + count3 + count4 + count5 + count6 + count7 +count8 + sky0_10 + sky10_30 + sky30_50 + sky50_90 +content, data=m2)
#summary(reg_poly5_full)
#coeftest(reg_poly5_full, vcov = vcovHC(reg_poly5_full, "HC1"))

#Main specification of 8th order Polynomial logs
reg_poly5_full = glm(ln_ChatsInBlock ~ as.factor(Hour) + as.factor(ChatDOW) + count + count2 + count3 + count4 + count5 + count6 + count7 +count8 + sky0_10 + sky10_30 + sky30_50 + sky50_90 +content, data=m2)
#summary(reg_poly5_full)
#coeftest(reg_poly5_full, vcov = vcovHC(reg_poly5_full, "HC1"))


#Main specification of 8th order Polynomial hour by day levels, HOD*DOW
reg_poly5_full = glm(ChatsInBlock ~ as.factor(Hour)*as.factor(ChatDOW) + count + count2 + count3 + count4 + count5 + count6 + count7 +count8 + sky0_10 + sky10_30 + sky30_50 + sky50_90 +content, data=m2)
#summary(reg_poly5_full)
#coeftest(reg_poly5_full, vcov = vcovHC(reg_poly5_full, "HC1"))

#Main specification of 8th order Polynomial hour by day logs, HOD*DOW
reg_poly5_full = glm(ln_ChatsInBlock ~ as.factor(Hour)*as.factor(ChatDOW) + count + count2 + count3 + count4 + count5 + count6 + count7 +count8 + sky0_10 + sky10_30 + sky30_50 + sky50_90 +content, data=m2)
#summary(reg_poly5_full)
#coeftest(reg_poly5_full, vcov = vcovHC(reg_poly5_full, "HC1"))

##################################################


#Control for day of month fixed effects (A&B likely varies within month)
#m1$DOM <-as.numeric(days(m1$dt))
#m1$early_month <- ifelse(m1$DOM < 6,1,0)

#8th order Polynomial with early month
#reg_poly6_early_full = glm(ChatsInBlock ~ as.factor(Hour) + as.factor(ChatDOW) + count + count2 + count3 + count4 + count5 + count6 + count7 + count8 + sky0_10 + sky10_30 + sky30_50 + sky50_90 +content, data=m2)
#summary(reg_poly6_early_full)
#coeftest(reg_poly6_early_full, vcov = vcovHC(reg_poly6_early_full, "HC1"))
```



######################################
##### Individual breaks with linear time trend on both sides
######################################
#Location in column where rollout occurs
#m1$sky0_10 <- ifelse(m1$dt >= "2016-10-11 00:00:00",1,0)
#m1$sky30_50 <- ifelse(m1$dt >= "2016-11-01 00:00:00",1,0)
#m1$content <- ifelse(m1$dt >= "2016-11-17 00:00:00",1,0)
#m1$sky50_90 <- ifelse(m1$dt >= "2016-12-15 00:00:00",1,0)
###########################



###############################
# Choose one week on either side of these breaks
#
# Third break
###############################

```{r}
break3<-"2016-11-01"
msky3 <-subset(m2,m2$dt >= as.POSIXct("2016-10-25",tz=tztz))
msky3 <-subset(msky3,msky3$dt < as.POSIXct("2016-11-08",tz=tztz))
msky3$sky30_50 <- ifelse(msky3$dt >= break3,1,0)


#Create linear time trend before and after
temp_data <- msky3[c("dt","ChatsInBlock")]
daily <- aggregate(. ~ cut(temp_data$dt, "1 day"), temp_data[setdiff(names(temp_data), "dt")], sum)
colnames(daily)[1] <- "daily_time"

daily$daily_time <- as.POSIXct(daily$daily_time, format = "%Y-%m-%d %H:%M:%S")
sky3<-which(grepl(break3, daily$daily_time))
#daily$date_formatted <- as.Date(daily$daily_time)
daily$linear1 <- seq(length(daily$ChatsInBlock))
daily$linear2 <- daily$linear1 -(sky3-1) 
daily$linear1 <- ifelse(daily$daily_time >= break3,0,daily$linear1)
daily$linear2 <- ifelse(daily$daily_time < break3,0,daily$linear2)

#Daylight savings time for this break makes things a bit odd to deal with so must drop extra dates
daily <-subset(daily,daily$daily_time < as.POSIXct("2016-11-08",tz=tztz))
msky3 <-subset(msky3,msky3$dt < as.POSIXct("2016-11-08",tz=tztz))

# Create subsets of data to merge
vars <- c("daily_time","linear1", "linear2")
temp <- daily[vars]

#Convert to a single date variable
msky3$date_only<- as.Date(msky3$dt, tz = tztz)
#utils::view(msky3)
temp$date_only<- as.Date(temp$daily_time, tz = tztz)
msky3_linear <- merge(temp,msky3, by= "date_only")
msky3_linear <- msky3_linear[with(msky3_linear, order(dt)), ]
#utils::view(msky3_linear)

##### Linear regression
reg_linear_sky3 = glm(ChatsInBlock ~ as.factor(Hour)  + linear1+ linear2+ sky30_50 , data=msky3_linear)
#summary(reg_linear_sky3)
#coeftest(reg_linear_sky3, vcov = vcovHC(reg_linear_sky3, "HC1"))

##### Linear regression
reg_linear_sky3 = glm(ln_ChatsInBlock ~ as.factor(Hour)  + linear1+ linear2+ sky30_50 , data=msky3_linear)
#summary(reg_linear_sky3)
#coeftest(reg_linear_sky3, vcov = vcovHC(reg_linear_sky3, "HC1"))

##### Linear regression
reg_linear_sky3 = glm(MeanChatDuration ~ as.factor(Hour)  + linear1+ linear2+ sky30_50 , data=msky3_linear)
#summary(reg_linear_sky3)
#coeftest(reg_linear_sky3, vcov = vcovHC(reg_linear_sky3, "HC1"))

msky3_linear$ln_MeanChatDuration<-log(msky3_linear$MeanChatDuration)
##### Linear regression
reg_linear_sky3 = glm(ln_MeanChatDuration ~ as.factor(Hour)  + linear1+ linear2+ sky30_50 , data=msky3_linear)
#summary(reg_linear_sky3)
#coeftest(reg_linear_sky3, vcov = vcovHC(reg_linear_sky3, "HC1"))

##### Linear RESIDUAL PLOT on SKy3
reg_linear_sky3 = glm(ChatsInBlock ~ as.factor(Hour)  + linear1+ linear2, data=msky3_linear)
msky3_linear$resid_linear_sky3 <- resid(reg_linear_sky3)
plot(msky3_linear$dt, msky3_linear$resid_linear_sky3,  main = "Chat Initiations", xlab = "Date", ylab = "Residual Live Chats/Hour (Unique Linear trends, no dummy)")
abline(v=as.POSIXct(break3),col = "red")
head(msky3_linear)


##### Linear RESIDUAL PLOT on SKy3
reg_linear_sky3 = glm(MeanChatDuration ~ as.factor(Hour)  + linear1+ linear2, data=msky3_linear)
msky3_linear$resid_linear_sky3 <- resid(reg_linear_sky3)
plot(msky3_linear$dt, msky3_linear$resid_linear_sky3,  main = "Chat Initiations", xlab = "Date", ylab = "Residual Chat Duration (Unique Linear trends, no dummy)")
abline(v=as.POSIXct(break3),col = "red")
```


###############################
# Choose one week on either side of these breaks
# #m1$sky10_30 <- ifelse(m1$dt >= "2016-10-18 00:00:00",1,0)
###############################


```{r}
# Second break
break2<-"2016-10-18"
msky2 <-subset(m2,m2$dt >= as.POSIXct("2016-10-13",tz=tztz))
msky2 <-subset(msky2,msky2$dt < as.POSIXct("2016-10-25",tz=tztz))
msky2$sky10_30 <- ifelse(msky2$dt >= break2,1,0)


#Create linear time trend before and after
temp_data <- msky2[c("dt","ChatsInBlock")]
daily <- aggregate(. ~ cut(temp_data$dt, "1 day"), temp_data[setdiff(names(temp_data), "dt")], sum)
colnames(daily)[1] <- "daily_time"

daily$daily_time <- as.POSIXct(daily$daily_time, format = "%Y-%m-%d", tz = "America/Los_Angeles")
sky2<-which(grepl(break2, daily$daily_time))
#daily$date_formatted <- as.Date(daily$daily_time)
daily$linear1 <- seq(length(daily$ChatsInBlock))
daily$linear2 <- daily$linear1 -(sky2-1) 
daily$linear1 <- ifelse(daily$daily_time >= break2,0,daily$linear1)
daily$linear2 <- ifelse(daily$daily_time < break2,0,daily$linear2)

#Daylight savings time for this break makes things a bit odd to deal with so must drop extra dates
daily <-subset(daily,daily$daily_time < as.POSIXct("2016-10-23",tz=tztz))
msky2 <-subset(msky2,msky2$dt < as.POSIXct("2016-10-23",tz=tztz))

# Create subsets of data to merge
vars <- c("daily_time","linear1", "linear2")
temp <- daily[vars]

#Convert to a single date variable
msky2$date_only<- as.Date(msky2$dt, tz = "America/Los_Angeles")
#utils::view(msky2)
temp$date_only<- as.Date(temp$daily_time, tz = "America/Los_Angeles")
msky2_linear <- merge(temp,msky2, by= "date_only")
msky2_linear <- msky2_linear[with(msky2_linear, order(dt)), ]
#utils::view(msky2_linear)

##### Linear regression
reg_linear_sky3 = glm(ChatsInBlock ~ as.factor(Hour)  + linear1+ linear2+ sky10_30, data=msky2_linear)
#summary(reg_linear_sky3)
#coeftest(reg_linear_sky3, vcov = vcovHC(reg_linear_sky3, "HC1"))

##### Linear regression
reg_linear_sky3 = glm(ln_ChatsInBlock ~ as.factor(Hour)  + linear1+ linear2+ sky10_30 , data=msky2_linear)
#summary(reg_linear_sky3)
#coeftest(reg_linear_sky3, vcov = vcovHC(reg_linear_sky3, "HC1"))

##### Linear regression
reg_linear_sky3 = glm(MeanChatDuration ~ as.factor(Hour)  + linear1+ linear2+ sky10_30 , data=msky2_linear)
#summary(reg_linear_sky3)
#coeftest(reg_linear_sky3, vcov = vcovHC(reg_linear_sky3, "HC1"))

msky2_linear$ln_MeanChatDuration<-log(msky2_linear$MeanChatDuration)
##### Linear regression
reg_linear_sky3 = glm(ln_MeanChatDuration ~ as.factor(Hour)  + linear1+ linear2+ sky10_30 , data=msky2_linear)
#summary(reg_linear_sky3)
#coeftest(reg_linear_sky3, vcov = vcovHC(reg_linear_sky3, "HC1"))

##### Linear RESIDUAL PLOT on SKy2
reg_linear_sky3 = glm(ChatsInBlock ~ as.factor(Hour)  + linear1+ linear2, data=msky2_linear)
msky2_linear$resid_linear_sky3 <- resid(reg_linear_sky3)
plot(msky2_linear$dt, msky2_linear$resid_linear_sky3,  main = "Chat Initiations", xlab = "Date", ylab = "Residual Live Chats/Hour (Unique Linear trends, no dummy)")
abline(v=as.POSIXct(break2),col = "red")


##### Linear RESIDUAL PLOT on SKy2 Chat DUration
reg_linear_sky3 = glm(MeanChatDuration ~ as.factor(Hour)  + linear1+ linear2, data=msky2_linear)
msky2_linear$resid_linear_sky3 <- resid(reg_linear_sky3)
plot(msky2_linear$dt, msky2_linear$resid_linear_sky3,  main = "Chat Durations", xlab = "Date", ylab = "Residual Chat Duration (Unique Linear trends, no dummy)")
abline(v=as.POSIXct(break2),col = "red")
```

########################################

###############################
# Choose one week on either side of these breaks
# #m1$sky50_90 <- ifelse(m1$dt >= "2016-12-15 00:00:00",1,0)
###############################

```{r}
# Second break
break2<-"2016-12-15"
msky2 <-subset(m2,m2$dt >= as.POSIXct("2016-12-10",tz=tztz))
msky2 <-subset(msky2,msky2$dt < as.POSIXct("2016-12-21",tz=tztz))
msky2$sky10_30 <- ifelse(msky2$dt >= break2,1,0)


#Create linear time trend before and after
temp_data <- msky2[c("dt","ChatsInBlock")]
daily <- aggregate(. ~ cut(temp_data$dt, "1 day"), temp_data[setdiff(names(temp_data), "dt")], sum)
colnames(daily)[1] <- "daily_time"

daily$daily_time <- as.POSIXct(daily$daily_time, format = "%Y-%m-%d", tz = "America/Los_Angeles")
sky2<-which(grepl(break2, daily$daily_time))
#daily$date_formatted <- as.Date(daily$daily_time)
daily$linear1 <- seq(length(daily$ChatsInBlock))
daily$linear2 <- daily$linear1 -(sky2-1) 
daily$linear1 <- ifelse(daily$daily_time >= break2,0,daily$linear1)
daily$linear2 <- ifelse(daily$daily_time < break2,0,daily$linear2)

#Daylight savings time for this break makes things a bit odd to deal with so must drop extra dates
daily <-subset(daily,daily$daily_time < as.POSIXct("2016-12-20",tz=tztz))
msky2 <-subset(msky2,msky2$dt < as.POSIXct("2016-12-20",tz=tztz))

# Create subsets of data to merge
vars <- c("daily_time","linear1", "linear2")
temp <- daily[vars]

#Convert to a single date variable
msky2$date_only<- as.Date(msky2$dt, tz = "America/Los_Angeles")
#utils::view(msky2)
temp$date_only<- as.Date(temp$daily_time, tz = "America/Los_Angeles")
msky2_linear <- merge(temp,msky2, by= "date_only")
msky2_linear <- msky2_linear[with(msky2_linear, order(dt)), ]
#utils::view(msky2_linear)

##### Linear regression
reg_linear_sky3 = glm(ChatsInBlock ~ as.factor(Hour)  + linear1+ linear2+ sky50_90, data=msky2_linear)
#summary(reg_linear_sky3)
#coeftest(reg_linear_sky3, vcov = vcovHC(reg_linear_sky3, "HC1"))

##### Linear regression
reg_linear_sky3 = glm(ln_ChatsInBlock ~ as.factor(Hour)  + linear1+ linear2+ sky50_90 , data=msky2_linear)
#summary(reg_linear_sky3)
#coeftest(reg_linear_sky3, vcov = vcovHC(reg_linear_sky3, "HC1"))

##### Linear regression
reg_linear_sky3 = glm(MeanChatDuration ~ as.factor(Hour)  + linear1+ linear2+ sky50_90 , data=msky2_linear)
#summary(reg_linear_sky3)
#coeftest(reg_linear_sky3, vcov = vcovHC(reg_linear_sky3, "HC1"))

msky2_linear$ln_MeanChatDuration<-log(msky2_linear$MeanChatDuration)
##### Linear regression
reg_linear_sky3 = glm(ln_MeanChatDuration ~ as.factor(Hour)  + linear1+ linear2+ sky50_90 , data=msky2_linear)
#summary(reg_linear_sky3)
#coeftest(reg_linear_sky3, vcov = vcovHC(reg_linear_sky3, "HC1"))

##### Linear RESIDUAL PLOT on SKy2
sky2_only<-which(grepl("2016-12-15", msky2_linear$dt))
reg_linear_sky3 = glm(ChatsInBlock ~ as.factor(Hour)  + linear1+ linear2, data=msky2_linear)
msky2_linear$resid_linear_sky3 <- resid(reg_linear_sky3)
plot(msky2_linear$dt, msky2_linear$resid_linear_sky3,  main = "Chat Initiations", xlab = "Date", ylab = "Residual Live Chats/Hour (Unique Linear trends, no dummy)")
abline(v=as.POSIXct(break2),col = "red")


##### Linear RESIDUAL PLOT on SKy2 Chat DUration
sky2_only<-which(grepl("2016-12-15", msky2_linear$dt))
reg_linear_sky3 = glm(MeanChatDuration ~ as.factor(Hour)  + linear1+ linear2, data=msky2_linear)
msky2_linear$resid_linear_sky3 <- resid(reg_linear_sky3)
plot(msky2_linear$dt, msky2_linear$resid_linear_sky3,  main = "Chat Durations", xlab = "Date", ylab = "Residual Chat Duration (Unique Linear trends, no dummy)")
abline(v=as.POSIXct(break2),col = "red")

#Raw Data
plot(msky2_linear$dt, msky2_linear$ChatsInBlock,  main = "Chat Initiations", xlab = "Date", ylab = "Chats/Hour")
abline(v=as.POSIXct(break2),col = "red")
```

##################
#  Full week around Dec 15 for DOW FEs
##################

###############################
# Choose one week on either side of these breaks
# #m1$sky50_90 <- ifelse(m1$dt >= "2016-12-15",1,0)
###############################

```{r}
# Second break
break2<-"2016-12-15"
msky2 <-subset(m2,m2$dt >= as.POSIXct("2016-12-08",tz=tztz))
msky2 <-subset(msky2,msky2$dt < as.POSIXct("2016-12-23",tz=tztz))
msky2$sky10_30 <- ifelse(msky2$dt >= break2,1,0)


#Create linear time trend before and after
temp_data <- msky2[c("dt","ChatsInBlock")]
daily <- aggregate(. ~ cut(temp_data$dt, "1 day"), temp_data[setdiff(names(temp_data), "dt")], sum)
colnames(daily)[1] <- "daily_time"

daily$daily_time <- as.POSIXct(daily$daily_time, format = "%Y-%m-%d", tz = "America/Los_Angeles")
sky2<-which(grepl(break2, daily$daily_time))
#daily$date_formatted <- as.Date(daily$daily_time)
daily$linear1 <- seq(length(daily$ChatsInBlock))
daily$linear2 <- daily$linear1 -(sky2-1) 
daily$linear1 <- ifelse(daily$daily_time >= break2,0,daily$linear1)
daily$linear2 <- ifelse(daily$daily_time < break2,0,daily$linear2)

#Daylight savings time for this break makes things a bit odd to deal with so must drop extra dates
daily <-subset(daily,daily$daily_time < as.POSIXct("2016-12-23",tz=tztz))
msky2 <-subset(msky2,msky2$dt < as.POSIXct("2016-12-23",tz=tztz))

# Create subsets of data to merge
vars <- c("daily_time","linear1", "linear2")
temp <- daily[vars]

#Convert to a single date variable
msky2$date_only<- as.Date(msky2$dt, tz = "America/Los_Angeles")
#utils::view(msky2)
temp$date_only<- as.Date(temp$daily_time, tz = "America/Los_Angeles")
msky2_linear <- merge(temp,msky2, by= "date_only")
msky2_linear <- msky2_linear[with(msky2_linear, order(dt)), ]
#utils::view(msky2_linear)

##### Linear regression
reg_linear_sky3 = glm(ChatsInBlock ~ as.factor(Hour) + ChatDOW + linear1+ linear2+ sky50_90, data=msky2_linear)
#summary(reg_linear_sky3)
#coeftest(reg_linear_sky3, vcov = vcovHC(reg_linear_sky3, "HC1"))

##### Linear regression
reg_linear_sky3 = glm(ln_ChatsInBlock ~ as.factor(Hour)  + ChatDOW +linear1+ linear2+ sky50_90 , data=msky2_linear)
#summary(reg_linear_sky3)
#coeftest(reg_linear_sky3, vcov = vcovHC(reg_linear_sky3, "HC1"))

##### Linear regression
reg_linear_sky3 = glm(MeanChatDuration ~ as.factor(Hour)  + ChatDOW +linear1+ linear2+ sky50_90 , data=msky2_linear)
#summary(reg_linear_sky3)
#coeftest(reg_linear_sky3, vcov = vcovHC(reg_linear_sky3, "HC1"))

msky2_linear$ln_MeanChatDuration<-log(msky2_linear$MeanChatDuration)
##### Linear regression
reg_linear_sky3 = glm(ln_MeanChatDuration ~ as.factor(Hour)  + ChatDOW +linear1+ linear2+ sky50_90 , data=msky2_linear)
#summary(reg_linear_sky3)
#coeftest(reg_linear_sky3, vcov = vcovHC(reg_linear_sky3, "HC1"))

##### Linear RESIDUAL PLOT on SKy2
reg_linear_sky3 = glm(ChatsInBlock ~ as.factor(Hour)  +ChatDOW + linear1+ linear2, data=msky2_linear)
msky2_linear$resid_linear_sky3 <- resid(reg_linear_sky3)
plot(msky2_linear$dt, msky2_linear$resid_linear_sky3,  main = "Chat Initiations", xlab = "Date", ylab = "Residual Live Chats/Hour (Unique Linear trends, no dummy)")
abline(v=as.POSIXct(break2),col = "red")


##### Linear RESIDUAL PLOT on SKy2 Chat DUration
reg_linear_sky3 = glm(MeanChatDuration ~ as.factor(Hour)  + ChatDOW +linear1+ linear2, data=msky2_linear)
msky2_linear$resid_linear_sky3 <- resid(reg_linear_sky3)
plot(msky2_linear$dt, msky2_linear$resid_linear_sky3,  main = "Chat Durations", xlab = "Date", ylab = "Residual Chat Duration (Unique Linear trends, no dummy)")
abline(v=as.POSIXct(break2),col = "red")

#Raw Data
plot(msky2_linear$dt, msky2_linear$ChatsInBlock,  main = "Chat Initiations", xlab = "Date", ylab = "Chats/Hour")
abline(v=as.POSIXct(break2),col = "red")
```


#############################
#####  Content Change
#m1$dum4 <- ifelse(m1$dt >= "2016-11-17",1,0)
#############################

```{r}
# Second break
break2<-"2016-11-17"
msky2 <-subset(m2,m2$dt >= as.POSIXct("2016-11-13",tz=tztz))
msky2 <-subset(msky2,msky2$dt < as.POSIXct("2016-11-22",tz=tztz))
msky2$sky10_30 <- ifelse(msky2$dt >= break2,1,0)


#Create linear time trend before and after
temp_data <- msky2[c("dt","ChatsInBlock")]
daily <- aggregate(. ~ cut(temp_data$dt, "1 day"), temp_data[setdiff(names(temp_data), "dt")], sum)
colnames(daily)[1] <- "daily_time"

daily$daily_time <- as.POSIXct(daily$daily_time, format = "%Y-%m-%d", tz = "America/Los_Angeles")
sky2<-which(grepl(break2, daily$daily_time))
#daily$date_formatted <- as.Date(daily$daily_time)
daily$linear1 <- seq(length(daily$ChatsInBlock))
daily$linear2 <- daily$linear1 -(sky2-1) 
daily$linear1 <- ifelse(daily$daily_time >= break2,0,daily$linear1)
daily$linear2 <- ifelse(daily$daily_time < break2,0,daily$linear2)

#Daylight savings time for this break makes things a bit odd to deal with so must drop extra dates
daily <-subset(daily,daily$daily_time < as.POSIXct("2016-11-21",tz=tztz))
msky2 <-subset(msky2,msky2$dt < as.POSIXct("2016-11-21",tz=tztz))

# Create subsets of data to merge
vars <- c("daily_time","linear1", "linear2")
temp <- daily[vars]

#Convert to a single date variable
msky2$date_only<- as.Date(msky2$dt, tz = "America/Los_Angeles")
#utils::view(msky2)
temp$date_only<- as.Date(temp$daily_time, tz = "America/Los_Angeles")
msky2_linear <- merge(temp,msky2, by= "date_only")
msky2_linear <- msky2_linear[with(msky2_linear, order(dt)), ]
#utils::view(msky2_linear)

##### Linear regression
reg_linear_sky3 = glm(ChatsInBlock ~ as.factor(Hour) +  linear1+ linear2+ content, data=msky2_linear)
#summary(reg_linear_sky3)
#coeftest(reg_linear_sky3, vcov = vcovHC(reg_linear_sky3, "HC1"))

##### Linear regression
reg_linear_sky3 = glm(ln_ChatsInBlock ~ as.factor(Hour)  + linear1+ linear2+ content , data=msky2_linear)
#summary(reg_linear_sky3)
#coeftest(reg_linear_sky3, vcov = vcovHC(reg_linear_sky3, "HC1"))

##### Linear regression
reg_linear_sky3 = glm(MeanChatDuration ~ as.factor(Hour)   +linear1+ linear2+ content , data=msky2_linear)
#summary(reg_linear_sky3)
#coeftest(reg_linear_sky3, vcov = vcovHC(reg_linear_sky3, "HC1"))

msky2_linear$ln_MeanChatDuration<-log(msky2_linear$MeanChatDuration)
##### Linear regression
reg_linear_sky3 = glm(ln_MeanChatDuration ~ as.factor(Hour)   +linear1+ linear2+ content , data=msky2_linear)
#summary(reg_linear_sky3)
#coeftest(reg_linear_sky3, vcov = vcovHC(reg_linear_sky3, "HC1"))

##### Linear RESIDUAL PLOT on SKy2
reg_linear_sky3 = glm(ChatsInBlock ~ as.factor(Hour)   + linear1+ linear2, data=msky2_linear)
msky2_linear$resid_linear_sky3 <- resid(reg_linear_sky3)
plot(msky2_linear$dt, msky2_linear$resid_linear_sky3,  main = "Chat Initiations", xlab = "Date", ylab = "Residual Live Chats/Hour (Unique Linear trends, no dummy)")
abline(v=as.POSIXct(break2),col = "red")


##### Linear RESIDUAL PLOT on SKy2 Chat DUration
reg_linear_sky3 = glm(MeanChatDuration ~ as.factor(Hour)  +linear1+ linear2, data=msky2_linear)
msky2_linear$resid_linear_sky3 <- resid(reg_linear_sky3)
plot(msky2_linear$dt, msky2_linear$resid_linear_sky3,  main = "Chat Durations", xlab = "Date", ylab = "Residual Chat Duration (Unique Linear trends, no dummy)")
abline(v=as.POSIXct(break2),col = "red")

#Raw Data
plot(msky2_linear$dt, msky2_linear$ChatsInBlock,  main = "Chat Initiations", xlab = "Date", ylab = "Chats/Hour")
abline(v=as.POSIXct(break2),col = "red")

#Raw Data
plot(daily$daily_time, daily$ChatsInBlock,  main = "Chat Initiations", xlab = "Date", ylab = "Chats/Hour")
abline(v=as.POSIXct(break2),col = "red")
```


#############################
#####  Changes in volume by week
#############################

```{r echo=F}
elap <- as.numeric((Sys.time()-starttime)[1],units="secs")
print(sprintf("%s created on %s took %.1f secs",versionstring,startfmttime,elap))
```
